\documentclass[main.tex]{subfiles}
\input{ExtraDefinitions.tex}

\begin{document}
%\renewcommand{\chaptername}{}
%\renewcommand{\thechapter}{}
%\renewcommand{\thetable}{A.\arabic{table}}
%\renewcommand{\thesection}{B.\arabic{section}}
%\renewcommand{\thesubsection}{C.\arabic{subsection}}
%\renewcommand{\theequation}{A.\arabic{equation}}
\renewcommand{\theequation}{A.\arabic{equation}}

\chapter[Optimised IBP reduction for many permuted families]{Optimised IBP reduction for amplitudes with many permuted families} \label{app:altIBPs}
In this appendix, we discuss how we can incorporate the IBP reduction in our workflow in a more efficient way, particularly when the amplitude includes many permutations of the same integral families. We exploit this method when computing the amplitudes presented in Chapter~\ref{sec:QEDpaper}.
\begin{figure}
    \centering
    \begin{adjustbox}{minipage=\textwidth,scale=0.9}
    \raisebox{0.2cm}{
    \begin{subfigure}[b]{0.25\linewidth}
        \hspace{-1cm}
        \begin{tikzpicture}
    	\begin{feynman}[small]
    		\vertex (v1);
    		\vertex[above left = 0.8cm of v1] (i1) {$p_5$};
    		\vertex[right = of v1] (v2);
    		\vertex[yshift=0.3cm, right = 0.8cm of v2] (v3);
    		\vertex[above right = 0.8cm of v3] (f1) {$p_1$};			
    		
    		\vertex[below = of v1] (v7) ;
    		\vertex[below left = 0.8cm of v7] (i2) {$p_4$};
    		\vertex[right = of v7] (v6) ;
    		\vertex[yshift=-0.3cm, right = 0.8cm of v6] (v5) ;
    		\vertex[below right = 0.8cm of v5] (f3) {$p_3$};
    		
    		\vertex[xshift=0.6cm, yshift=0.2cm, below = of v3] (v4);
    		\vertex[right = 0.8cm of v4] (f2) {$p_2$};		

            \draw ($(v1)!0.5!(v2)$) node[cross,red] (5cm) {};
            \draw ($(v4)!0.5!(v3)$) node[cross,red,rotate=45] (5cm) {};
            
    		\diagram*{
    			(i1) -- [very thick] (v1) -- (v2) -- (v3),
    			(i2) -- (v7) -- (v6) -- (v5),
    			(v3) -- (f1),
    			(v3) -- (v4) -- (v5),
    			(v4) -- (f2),
    			(v5) -- (f3),
    			(v1) -- (v7),
    			(v2) -- (v6),
    		};
    	\end{feynman}
    \end{tikzpicture}
    \caption{} \label{fig:pentabox}
    \end{subfigure}
    }
    %\end{adjustbox}
    \hspace{1.3cm}
    %\begin{adjustbox}{minipage=\linewidth,scale=0.4}
    \begin{subfigure}[b]{0.25\linewidth}
        \hspace{-1cm}
        \begin{tikzpicture}
        \begin{feynman}[small]
			\vertex (v1);
			\vertex[left = 0.8cm of v1] (i1) {$p_4$};
			\vertex[above right =1cm of v1] (v2);
			\vertex[below right =1cm of v1] (v3);				
			\vertex[yshift=0.3cm, right = 0.7cm of v2] (v4);	
			\vertex[yshift=-0.6cm, right = 0.7cm of v4] (v5);
			\vertex[yshift=-0.3cm, right = 0.7cm of v3] (v7);
			\vertex[yshift=0.6cm, right = 0.7cm of v7] (v6);	
			\vertex[above right = 0.8cm of v4] (i2) {$p_5$};
			\vertex[yshift=0.2cm, right = 0.8cm of v5] (i3) {$p_2$};
			\vertex[yshift=-0.2cm, right = 0.8cm of v6] (i4) {$p_1$};
			\vertex[below right = 0.8cm of v7] (i5) {$p_3$};
			
            \draw ($(v5)!0.5!(v6)$) node[cross,red] (5cm) {};
            \draw ($(v2)!0.5!(v4)$) node[cross,red, rotate=30] (5cm) {};
            
			\diagram*{
				(i1) -- (v1) -- (v2) -- (v3) -- (v1),
				(v2) -- (v4) -- (v5) -- (v6) -- (v7) -- (v3),
				(v4) -- [very thick] (i2),
				(v5) -- (i3),
				(v6) -- (i4),
				(v7) -- (i5),
			};
		\end{feynman}
        \end{tikzpicture}
    \caption{} \label{fig:hexatriangle}
    \end{subfigure}
    %\end{adjustbox}
    \hspace{1.3cm}
    %\begin{adjustbox}{minipage=\linewidth,scale=0.4}
    \raisebox{0.2cm}{
    \begin{subfigure}[b]{0.25\linewidth}
        \hspace{1em}
        \begin{tikzpicture}
    	\begin{feynman}[small]
    		\vertex (v1);
      
    		\vertex[left = 0.8cm of v1] (i1) {$p_4$};
    		\vertex[above right = of v1] (v2);			
    		\vertex[below right = of v1] (v3);			
    		\vertex[right = of v2] (v4);			
    		\vertex[right = of v3] (v5);			
    		
    		\vertex[below right = 0.8cm of v5] (i2) {$p_3$};
    		\vertex[above right = 0.6cm of v4, xshift=0.2cm, yshift=-0.2cm] (i3) {$p_2$};
    		\vertex[above right = 0.4cm of v4, yshift=+0.4cm] (i4) {$p_1$};
    		\vertex[above =  0.7cm of v2] (i5) {$p_5$};
    		
    		\diagram*{
                (i1) -- (v1) -- (v2) -- (v4),
                (v1) -- (v3) -- (v5) -- (i2),
                (v2) -- (v3),
                (v4) -- (v5),
                (v4) -- (i3),
                (v4) -- (i4),
                (v2) -- [very thick] (i5),
    		};
    	\end{feynman}
    \end{tikzpicture}
    \caption{}
    \end{subfigure}
    }
    \end{adjustbox}
\caption{A simple example of possible non-IBP relations between integrals within different (maximal) topologies. Integrals in lower sectors often map to each other. The bold line indicates the massive momentum, $p_5$, while red crosses denote a removed denominator, i.e. the corresponding $\nu_i$ is 0. Here, diagrams $(a)$ and $(b)$ both collapse onto diagram $(c)$. Such relations are often hard to discover just from analysing the propagators of the integrals, especially if the two families use vastly different conventions for loop momentum routing. However, a visual representation often makes spotting these relations trivial.}
\label{fig:symmetryrelation}
\end{figure}
We start by pointing out a certain fact related to Eq.~\ref{eq:ampafterIBP}: the number of MIs for all families considered together is not the same as the sum of numbers of MIs for these families considered separately. That is:
\begin{equation} \label{eq:noofmis}
    |\text{MI}| \equiv |\text{MI}_{\bigcup_T}| \le \sum_{\mathclap{\substack{T \in \\ \text{maximal} \\ \text{topologies}}}} |\text{MI}_T| \,,
\end{equation}
where $\bigcup_T$ indicates the union of all maximal topologies $T$. This statement might seem somewhat surprising. Indeed, if we formulate one big system of IBP relations between integrals in all the families and perform the IBP reduction, the resultant MI basis is equal to the sum of the bases obtained by solving smaller systems of IBP relations within each family one by one. This is because IBP relations, by construction, cannot include integrals from different families. However, it turns out that integrals belonging to sectors other than the top sector can often be mapped between families (see  Fig.~\ref{fig:symmetryrelation} for an easy to understand example). Therefore, an amplitude reduced using $N_T$ separate IBP systems contains leftover MIs that can be further reduced onto each other with the help of non-IBP mappings. To avoid this redundancy, we typically build a combined system which covers all the families in the problem. It contains the pure IBP relations, as well as the additional inter-family mappings\footnote{In practice, these mappings are found by comparing integrals based on their representation in terms of the $\mathcal{U}$ and $\mathcal{F}$ Symanzik polynomials (see Section 4 of Ref.~\cite{Lee:2012cn} and also Ref.~\cite{Pak:2011xt}).}. Unfortunately, for large $N_T$, this often leads to a prohibitively expensive computation and may even constitute the main bottleneck of the whole workflow.

There is, however, a more efficient way of performing the reduction. Recall that the integral families fed into the reduction are defined by their propagators and ISPs. Specialising to the five-particle case, each family can therefore be denoted as $T(ijklm)$, where $T$ is the family type and $ijklm$ is an ordering of the external momenta within that type (understood as $ijklm \equiv p_i,\ldots, p_m$). Note that in the presence of an internal or external mass, we need to further distinguish between topology subtypes based on the position of this mass. For example, we refer to the topology of Fig.~\ref{fig:pentabox} as `zzz penta-box$(12345)$', and to that of Fig.~\ref{fig:hexatriangle} as `mzz hexa-triangle$(52134)$' (we follow the naming convention of Ref.~\cite{Abreu:2020jxa}).

Consider two families which are of the same (sub)type and differ only by a permutation $\sigma \equiv (\sigma_i, \ldots, \sigma_m)$ which preserves the position of any massive legs. Then, we can write $T'=(\sigma \circ T)(ijklm) = T(\sigma_i, \ldots, \sigma_m)$ and the IBP reduction of any integral $I_{T'}(\bm{\nu})$ can be expressed by permuting the reduction of $I_T(\bm{\nu})$ according to $\sigma$:
\begin{align} \label{eq:IBPpermutations}
    I_{T(ijklm)}(\bm{\nu}) &= \sum_{i=1}^{|\text{MI}_T|} c_i(p, \eps) \times \text{MI}_{T(ijklm),\,i} \nonumber \\
    \implies I_{T'}(\bm{\nu}) &= \sum_{i=1}^{|\text{MI}_T|} c_i(\sigma(p), \eps) \times \text{MI}_{T^\prime,\,i}\,.
\end{align}
Here, $p$ denotes the collective dependence on the external momenta $p_i, \ldots, p_m$, with $\sigma(p) \equiv p_{\sigma_i}, \ldots, p_{\sigma_m}$. The new reduction coefficients $c^\prime_i = c_i(\sigma(p), \eps)$ are computed as a permutation of the external kinematics in the old coefficients $c_i(p, \eps)$, while the new master integrals MI$_{T^\prime}$ are obtained by permuting the external momenta in the propagators and ISPs of MI$_T$\footnote{In the case of pure MIs, which are often defined as combinations of integrals $I_T$, we also need to permute any potential kinematic prefactor of these integrals according to $\sigma$.}.

In our applications, the reduction coefficients $c_i$ will most often be parametrised by the momentum twistors $\mathbf{x}$. Then, since they will be rational functions of $\mathbf{x}$ and $\eps$, permuting the external kinematics to obtain $c_i^\prime$ is trivial. Moreover, the rationality means that this approach to IBP reduction is perfectly compatible with the finite field sampling procedure. From Eq.~\ref{eq:IBPpermutations}, we can see that permuting the coefficients amounts to evaluating them at a permuted phase-space point. This is also equivalent to a change of the kinematic variables, which is an operation that can be easily implemented in \texttt{FiniteFlow}\footnote{When working with the $s_{ij}$ variables, the permutation $s_{\sigma(ij)}$ will in general take us outside of their minimal set, but we can always express the new Mandelstam variables through the same minimal set using momentum conservation and on-shell conditions.}~\cite{Peraro:2019svx}. Thus, we never have to know and permute the analytic form of the coefficients, which leads to a significant reduction in the computational cost. Overall, for an integral family with $n$ massless particles, we do not need to explicitly perform the IBP reduction in up to $n!$ permutations of it. In fact, we only need to do it once --- in an arbitrarily chosen permutation of this family, which we label $T(\sigma_\text{id})$. Then, the reduction of any permutation of this family is obtained by considering $\sigma$ such that $\sigma \circ \sigma_\text{id}$ brings us onto the target family, that is $T' = (\sigma \circ T)(\sigma_\text{id})$, and applying the steps above.

Let us now discuss a small issue with this new strategy. As pointed out in the beginning of this section, the total number of MIs after the reduction is smaller than the sum of MIs in the individual families. This redundancy is not taken care of in the approach we have described above, since the reduction is performed only within the ‘main’ families $T(\sigma_\text{id})$ and then permuted to cover all needed permutations. Thus, the inter-family mappings between the MIs are not found and the reduced amplitude will contain MIs which are in fact not fully linearly independent. Strictly speaking, there is no requirement for the amplitude to be expressed in terms of independent objects. However, it is desirable to do so, as this ensures that any cancellations happen analytically and prevents instabilities or issues with precision during the numerical evaluation of the amplitude. Moreover, it is more computationally efficient, as it reduces the number of independent coefficients that have to be processed when expanding the amplitude into special functions (see Section~\ref{sec:specialfunctions}).

In practice, we obtain these missing relations between MIs by performing \textit{their} reduction in the `traditional' approach (i.e. all families included together in one system) in \texttt{LiteRed}. This expresses the MIs from all families in terms of the truly independent ones:
\begin{equation} \label{eq:mappings}
    \text{MI}_{i} = \sum_j^{|\text{MI}|} f_{ij}(p, \eps) \times \text{MI}_j \qquad i \in \left\{1, \ldots, \sum_T |\text{MI}_T|\right\}\,.
\end{equation}
Here, $i$ runs over the `naive' MIs of all maximal topologies and $|\text{MI}|$ is the number of truly independent MIs in the sense of Eq.~\ref{eq:noofmis}. We stress that this additional reduction of the naive MIs does not present such a high complexity as the reduction needed for the amplitude itself. Firstly, the identities generated through the Laporta algorithm only need to cover the rank and number of dotted propagators present in the MI bases, rather than the full amplitude. Secondly, an extremely useful property of UT integrals\footnote{We discuss the UT property of integrals in Section~\ref{sec:UT}.} is that any linear relation between them cannot contain a dependence on the kinematic variables, i.e. $f(p, \eps) \rightarrow f(\eps)$ in Eq.~\ref{eq:mappings}. This is simply because adding such kinematic factors would break the canonical form of the DEs and would imply that at least one of these integrals was not in fact UT. Thus, when using UT bases, which has become the standard in modern amplitude computations, this additional reduction can be performed with the kinematic variables set to random numeric values (subject to momentum conservation). Finally, all the missing relations between MIs can be worked out once and for all --- they will be applicable to any process at the same loop order and number of particles (and masses), since the IBP reduction is specific only to the kinematic setup.

Having obtained the missing relations between the naive MIs, we apply them to our amplitude and collect the coefficients of the true, linearly independent MIs. Overall, we find that this alternative approach performs much better than the previously employed strategy of considering all integral families together in one shared system. The benefit grows with the number of permutations of the maximal topologies, since including additional families in the IBP system is expensive, but numerically permuting the solution from one family onto another is cheap.

\renewcommand{\theequation}{B.\arabic{section}.\arabic{equation}}
\chapter{Symbols} \label{app:symbols}
\section{Introduction}
In this appendix, we introduce another useful concept related to DEs and iterated integrals. We begin by noting that the representation of the solution to the $\eps$-form DEs in Eq.~\ref{eq:canonicalDEsoneform} is not unique. Most generally, the answer is written using Chen's iterated integrals (CIIs)~\cite{Chen:1977oja}. However, as pointed out above Eq.~\ref{eq:GPLs}, if the `letters' are rational in at least one variable, CIIs can be expressed in terms of GPLs~\cite{Henn:2014qga}. This has the advantage that robust and stable numerical evaluation of GPLs is available (see Refs.~\cite{Bauer:2000cp, Vollinga:2004sn, Panzer:2014caa}). On the downside, contrary to CIIs, GPLs contain a large degree of redundancy in the sense that they satisfy extra functional relations, obscuring possible simplifications and cancellations. Other representations apart from CIIs and GPLs are also possible. Due to the conjecture pointed out in Section~\ref{sec:UT}, typically we will be interested in computing the DE solution up to transcendental weight 4. Another remarkable conjecture exists: any transcendental function of weight $k < 4$ can be expressed in terms of the usual logarithms and polylogarithms $\text{Li}_k$ only~\cite{MR1265551, Goncharov:2010jf}, while at weight $k=4$ all functions can be expressed in terms of $\Li_4(x), \Li_{2,2}(x,y)$ and weight-4 products of lower-weight functions\footnote{See Section 6 of Ref.~\cite{Duhr:2011zq}, which considers this problem for the spanning set of functions with $k\le4$ in the special case of Harmonic Polylogarithms (GPLs with all indices $a_i\in\{0,\pm1\})$.}~\cite{Henn:2014qga}. 
%\begin{equation} \label{eq:weight4basis}
%    \left\{\log(x)\log(y)\log(z)\log(w), \Li_2(z) \log(x) \log(y), \Li_2(x)\Li_2(y), \Li_3(y) \log (x), \Li_4(x), \Li_{2,2}(x, y) \right\}\,,
%\end{equation}
%here, the arguments $x,y,z,w$ are to be determined.
Here, the classical polylogarithms $\Li_n(z)$ are defined as:
\begin{equation} \label{eq:Lidefinition}
    \Li_n(z) = \sum_{k=1}^\infty \frac{z^k}{k^n}\,, \qquad |z|<1,\,\, n \in \mathbb{N}\,,
\end{equation}
while the multiple polylogarithms (MPLs) $\Li_{m_1, \ldots, m_k}$ are their multi-index, multi-variable generalisations~\cite{2011arXiv1105.2076G, Duhr:2019tlz}:
\begin{subequations}
\begin{align} \label{eq:multiLidefinition}
    \Li_{m_1, \ldots, m_n}(z_1, \ldots, z_n) &= \sum_{0<k_1<\ldots<k_n} \frac{z_1^{k_1} \ldots z_n^{k_n}}{k_1^{m_1} \ldots k_n^{m_n}} \\
    &= \sum_{k_n=1}^\infty \frac{z_n^{k_n}}{k_n^{m_n}} \sum_{k_{n-1}=1}^{k_n-1} \frac{z_{n-1}^{k_{n-1}}}{k_{n-1}^{m_{n-1}}}\ldots \sum_{k_1=1}^{k_2-1} \frac{z_1^{k_1}}{k_1^{m_1}}\,, \qquad |z_i|<1, \,\, m_i \in \mathbb{N} \,. \label{eq:multiLidefinition2}
\end{align}
\end{subequations}
Note that in these two definitions, $|z_i|<1$, but the functions can be analytically continued to cover regions where $|z_i| \ge 1$. The $\Li_{m_1, \ldots, m_k}$ MPLs can be viewed as the series representation of the GPLs defined in Eq.~\ref{eq:GPLs}. They are related through the following equation~\cite{Duhr:2011zq}:
\begin{equation} \label{eq:LiToG}
    \Li_{m_1, \ldots, m_n}(z_1, \ldots, z_n) = (-1)^n\,G\left(\vec{0}_{m_n-1}, \frac{1}{z_n}, \ldots, \vec{0}_{m_1-1}, \frac{1}{z_1\ldots z_n}; \,1 \right)\,,
\end{equation}
where $\vec{0}_m$ denotes a vector of zeros of length $m$. For example, the aforementioned $\Li_{2,2}(x, y)$ can be written as:%admits the integral representation:
\begin{equation}
     \Li_{2,2}(x, y) = G\left(0, \frac{1}{y}, 0, \frac{1}{xy};\,1 \right)\,.
\end{equation}
%\begin{equation}
%    \Li_{2,2}(x, y) = -\int_0^1 \frac{x \dd t}{1- xt} \log t \, \Li_2(xyt)\,.
%\end{equation}
Overall, the solution to the canonical DEs written in terms of special functions rather than CIIs is likely to contain a large degree of redundancy. Moreover, due to the abundance of representations, it is not easy to choose the most appropriate set of functions or even verify if two expressions are equivalent. We would like to have a tool which can find relations between transcendental functions and be representation independent. To this end, we introduce the notion of a `symbol'\cite{Goncharov:2010jf, Duhr:2011zq}. After giving its definition and properties, we will demonstrate its power based on several illustrative examples. To motivate our effort, we remark that the main result of Ref.~\cite{Goncharov:2010jf} was the application of the symbol to re-write a 17-page expression for a quantity known as the two-loop, six-point remainder function (related to Wilson loops) in $\mathcal{N}=4$ SYM~\cite{DelDuca:2009au, DelDuca:2010zg} as a remarkably compact combination of classical polylogarithms that fits on just a handful of lines.
\section{Definition and properties}
The symbol of a CII with $\dd \log$ kernels is defined as:
\begin{equation} \label{eq:symboldef}
    \SS \left(\int_\gamma \dd \log w_1 \cdot \ldots \cdot \dd \log w_n \right) \equiv w_1 \oo \ldots \oo w_n \,.
\end{equation}
We can think of it as an elementary $n$-fold tensor where each entry $w_i$ is implicitly understood as its corresponding $\dd \log$. It satisfies certain properties that we would expect from the behaviour of logarithms\footnote{For a detailed discussion of symbol properties, see Ref.~\cite{Duhr:2011zq}.}:
\begin{subequations} \label{eq:symbolproperties}
\begin{align}
    A \oo (ab) \oo B &= A \oo a \oo B + A \oo b \oo B\,, \\
    A \oo \left(\frac{a}{b}\right) \oo B &= A \oo a \oo B - A \oo b \oo B\,, \\
    A \oo a^n \oo B &= n(A \oo a \oo B)\,,
\end{align}
\end{subequations}
where $A, B$ are elementary tensors and $a, b$ are algebraic functions. Note that in the last line, $n$ becomes a coefficient in front of the symbol, rather than a part of it. Moreover, a symbol which contains a constant (not only rational) vanishes:
\begin{equation} \label{eq:symbolAcB}
    A \oo c \oo B = 0\,,
\end{equation}
which can be understood as a consequence of $\dd \log c = 0$. This means that, when working with the symbol, we are insensitive to constants, including transcendental ones like $\pi$. 

Since CIIs are defined as repeated integrations over some kernels (see Eq.~\ref{eq:CIIsdef}), the total differential acts on the symbol defined through Eq.~\ref{eq:symboldef} as:
\begin{equation} \label{eq:symboldiff}
    \dd (w_1 \oo \ldots \oo w_n) = \dd \log w_n \, (w_1 \oo \ldots \oo w_{n-1})\,.
\end{equation}
This property goes hand in hand with the definition of pure functions in Eq.~\ref{eq:purecondition}. Crucially, it can be reversed and allows us to define the symbol recursively~\cite{Goncharov:2010jf}. For a transcendental function $F$ with $\mathcal{T}(F) = k$ whose total differential can be written as:
\begin{equation} \label{eq:Ftofrecursive}
    \dd F = \sum_i f_i \, \dd \log w_i\,,
\end{equation}
where $f_i$ are functions with $\mathcal{T}(f_i)=k-1$, we have:
\begin{equation} \label{eq:symbolrecursive}
    \SS(F) = \sum_i \SS(f_i)\oo w_i \,.
\end{equation}
The starting point of the recursion is the `empty' symbol: $\SS(1)$. Let us see how to use this definition. For now, we will focus on the classical polylogarithms $\Li_n(z)$. In this case, we will need the symbol of a single weight-1 function --- the logarithm: $\SS(\log w) = w$, which can itself be obtained using Eqs.~\ref{eq:Ftofrecursive} and~\ref{eq:symbolrecursive}. Here, the $w$ on the RHS is understood as an elementary tensor in the sense of Eq.~\ref{eq:symboldef}. This immediately allows us to obtain the symbol of any $\Li_n$. Note that the weight-1 polylogarithm is just the normal logarithm:
\begin{equation} \label{eq:Li1equivlog}
    \Li_1(z) = -\log (1-z)\,. 
\end{equation}
Moreover, the following iterative definition holds:
\begin{equation} \label{eq:Liiterative}
    \Li_n(z) = \int_0^z \frac{\dd t}{t} \Li_{n-1}(t)\,, \qquad n>1\,,
\end{equation}
which is equivalent to the differential relation:
\begin{equation}
    \dd \Li_n(z) = (\dd \log z) \Li_{n-1}(z) \,, \qquad n>1\,.
\end{equation}
Thus, Eqs.~\ref{eq:symbolrecursive} and \ref{eq:Li1equivlog} give:
\begin{align} \label{eq:Lisymbols}
    \SS(\Li_1(z)) &= -(1-z)\,, \nonumber \\
    \SS(\Li_2(z)) &= -(1-z) \oo z \,, \nonumber \\
    &\,\,\, \vdots \nonumber \\
    \SS(\Li_n(z)) &= -(1-z) \oo \underbrace{z \oo \ldots \oo z}_{n-1 \text{ times}}\,.
\end{align}
Note that in deriving the first line, we used $\SS(-f) = -\SS(f)$ and this minus sign cannot be dropped or absorbed, i.e. $\SS(\Li_1(z)) \neq (z-1)$. Moreover, it should not be confused with the symbol expression $-1 \oo (1-z)$, which vanishes due to Eq.~\ref{eq:symbolAcB}. To avoid confusion, the symbol is often written using square brackets, e.g. $\SS(\Li_2(z)) = -[1-z, z]$.

The symbol of the GPLs can be obtained recursively in a similar manner. We will need the differential equivalent of the integral definition in Eq.~\ref{eq:GPLs} \cite{2001math......3059G}:
\begin{equation} \label{eq:GPLdifferential}
    \dd G(a_{n-1}, \ldots, a_1; a_n) = \sum_{i=1}^{n-1} G(a_{n-1}, \ldots, \hat{a}_i, \ldots, a_1; a_n) \, \dd \log\left( \frac{a_i - a_{i+1}}{a_i - a_{i-1}} \right)\,,
\end{equation}
where $a_1, \ldots, a_n$ are unique non-zero indices, $a_0$ is understood as 0 and $\hat{a}_i$ denotes the index that should be removed in a particular GPL. The starting point of the recursion is the symbol of the `empty' GPL, defined as the empty symbol: 
\begin{equation}
    \SS (G(;z)) = [\,]\,.
\end{equation}  
Clearly, the reader will now understand why we mentioned the alternative notation for the symbol. We can now move up on the recursion ladder by one step:
\begin{equation}
    \dd G(a; z) = G(;z) \, \dd \log \left(\frac{a-z}{a} \right)\,.
\end{equation}
Then, the weight-1 GPL has the symbol:
\begin{equation} \label{eq:G1symbol}
    \SS(G(a; z)) = \left[\frac{a-z}{a} \right] = [a-z] - [a]\,.
\end{equation}
Proceeding in this manner, we can then calculate the symbols of all GPLs with higher weights.

We also need to know how to obtain the symbol of a product of functions, e.g. $\SS(\log(z) \Li_2(z))$. To this end, we point out that the CIIs satisfy so-called shuffle relations\footnote{For this simple weight-3 function, its symbol can be obtained more directly by taking the differential and using Eq~\ref{eq:symbolrecursive}. Nonetheless, we find it illustrative to introduce the shuffle product, as it becomes useful in more complicated cases.}. Specialising to the case of GPLs, we have:
\begin{equation} \label{eq:GPLshuffleprod}
    G(\vec{a};z)G(\vec{b};z) = \sum_{\vec{c}=\vec{a} \shuffle \vec{b}} G(\vec{c};z)\,.
\end{equation}
The shuffle product $\vec{a} \shuffle \vec{b}$ denotes all possible ways of permuting the union of indices $\vec{a}$ and $\vec{b}$ such that the ordering of indices within each set is preserved. Perhaps a simple example illustrates this definition better:
\begin{align} \label{eq:shuffleexample}
    G(a_1,a_2;z) G(b_1,b_2;z) &= G(a_1,a_2,b_1,b_2;z) + G(a_1,b_1,a_2,b_2;z) + G(a_1,b_1,b_2,a_2;z) \nonumber \\ 
    & + G(b_1,a_1,a_2,b_2;z) + G(b_1,a_1,b_2,a_2;z) + G(b_1,b_2,a_1,a_2;z)\,.
\end{align}
Therefore, the shuffle relations allow us to write a product of GPLs of weight $|\vec{a}|$ and $|\vec{b}|$ as a linear combination of GPLs of weight $|\vec{a}|+|\vec{b}|$. Thus, we can now calculate the symbol of the product $\SS(\log(z) \Li_2(z))$ by expressing the two functions as special instances of GPLs, taking the shuffle product of these GPLs according to Eq.~\ref{eq:GPLshuffleprod} and finally mapping the symbol over the resultant sum of higher-weight GPLs. However, it is often easier to follow an alternative route, which arises due to the fact that:
\begin{equation}
    \SS(f_1 f_2) = \SS(f_1) \times \SS(f_2)\,,
\end{equation}
where the RHS is understood as the shuffle product of the individual symbols. Indeed, the symbol itself inherits the shuffle algebra:
\begin{equation} \label{eq:symbolshuffle}
    (w_1 \oo \ldots \oo w_n) \times (v_1 \oo \ldots \oo v_m) = \sum_{\vec{z}=\vec{w} \shuffle \vec{v}} (z_1 \oo \ldots \oo z_{n+m})\,.
\end{equation}
Therefore, in our example we may simply write: 
\begin{align}
    \SS(\log(z) \Li_2(z)) &= (z) \times (-(1-z)\oo z) \nonumber \\
    &= -z \oo (1-z) \oo z - 2 (1-z) \oo z \oo z \\
    &= -[z, 1-z, z] -2[1-z, z, z] \,. \nonumber
\end{align}
In the last line, we have again used the alternative notation in order to make the position of the minus sign and a constant absolutely clear.

\section{Examples}
Overall, we see that thanks to symbols of the classical polylogarithms, Eq.~\ref{eq:Lisymbols}, and GPLs, Eq.~\ref{eq:G1symbol}, as well as the symbol shuffling, Eq.~\ref{eq:symbolshuffle}, and finally the relation in Eq.~\ref{eq:LiToG}, we can now compute the symbol of any function that may appear in the weight-4 function basis. Thinking ahead to our amplitude applications, it is clear that the symbol will allow us to find relations between linearly dependent objects such as GPLs and express our results in a much more compact form. Having expended the effort of understanding the last few pages, let us enjoy the fruits of our labour sprouting in the form of several illustrative examples.

\textbf{Example 1} \newline
Given a functional relation, we can check its validity --- but only up to constants. More precisely, while we can never prove with full certainty that an identity is valid by looking at its symbols, we can definitely show that an identity is not correct by proving that the symbols do not match up. The symbols allow us to fix the most complicated part of the identities. What is left is essentially boundary values, which can be determined for example by evaluating both sides of the relation at a numerical point. Consider the well-known dilogarithm reflection identity:
\begin{equation}
    \Li_2(1-z) =- \Li_2(z) -\log(z) \log(1-z) + \frac{\pi^2}{6} \,,
\end{equation}
valid in the domain $z \in \mathbb{C} \setminus\{(-\infty, 0] \cup [1, \infty)\}$. For the two dilogarithms, we can straightforwardly use Eq.~\ref{eq:Lisymbols}, while for the product of ordinary logs we need to use the shuffle algebra. At the symbol level, the identity reads:
\begin{equation}
    -[z,1-z] = + [1-z,z] - [z] \shuffle [1-z]\,.
\end{equation}
Taking the shuffle product leaves the two sides equal. Thus, we managed to verify that the identity holds --- up the factor of $\pi^2/6$, which we can easily find by evaluating the rest of the identity at e.g. $z=1$.

\textbf{Example 2} \newline
If we're trying to construct a functional relation, the symbol can also help us to fix the coefficients of the functions. Let us conjecture another identity:
\begin{equation} \label{eq:Li2ref2conj}
    \Li_2\left( \frac{1}{z} \right) = a\,\Li_2(z) + b \log^2(-z) + c\,,
\end{equation}
where $a,b,c$ are rational constants. Then, at the symbol level:
\begin{align}
    -\left[1-\frac{1}{z}, \frac{1}{z}\right] &= -a[1-z, z] + b[-z] \shuffle [-z] \nonumber \\
    [z-1,z] - [z,z] &= -a[z-1, z] + 2 b[z]\,,
\end{align}
To get to the second line, we have expanded the LHS using the symbol properties in Eqs.~\ref{eq:symbolproperties} and \ref{eq:symbolAcB}, while on the RHS we used $[-x]=[x]$, which is a direct consequence of these properties. Thus, $a=-1, \, b=-1/2$. We still need to fix the so-called `beyond the symbol terms'. These include not only the weight-2 constants such as $\pi^2$, but also products of weight-1 constants with a $\log$. The latter type can be often fixed by differentiating both sides of the identity, thus producing a relation at a lower weight. In this case, differentiating Eq.~\ref{eq:Li2ref2conj} with the known values of $a$ and $b$ shows that no $\log \times \text{constant}$ terms are missing. Hence, only weight-2 constants are allowed in $c$ and we can fix it by evaluating the identity at a chosen value of $z$. In this way, we find:
\begin{equation} \label{eq:Li2ref2}
    \Li_2\left( \frac{1}{z} \right) = -\Li_2(z) - \frac{1}{2} \log^2(-z) - \frac{\pi^2}{6}\,, \qquad z \in \mathbb{C} \setminus [0,\, \infty)\,,
\end{equation}
which is indeed a well-known dilogarithm relation. Finally, the reader might wonder why we have conjectured $\log(-z)$ instead of $\log(z)$. After all, as pointed out above, both these functions have the same symbol --- $[z]$. The reason is simple: swapping the sign of the argument in the $\log$ would mean that there is no domain in which all the functions in this relation are well-defined and they would consequently have to be analytically continued.

\textbf{Example 3} \newline
For more complicated identities, calculating the symbol by hand becomes unfeasible. Consider the following weight-3 relation:
\begin{align}
    \Li_3(z)&=-\Li_3\left(\frac{z}{z-1}\right)-\Li_3(1-z) \nonumber \\
    &+\frac{1}{6} \log ^3(1-z)-\frac{1}{2} \log (z) \log ^2(1-z)+\frac{1}{6} \pi ^2 \log (1-z)+\zeta (3)\,,
\end{align}
which holds for $z \in \mathbb{C} \setminus\{(-\infty, 0] \cup [1, \infty)\}$. The symbol of the LHS is trivial thanks to Eq.~\ref{eq:Lisymbols}:
\begin{equation} \label{eq:Li3symbol}
    \SS(\Li_3(z)) = -[1-z,z,z]\,.
\end{equation}
The RHS requires much more work, namely repeated application of shuffle products and symbol properties in Eq.~\ref{eq:symbolproperties}. These operations can be easily automated, however. In particular, we make use of the \texttt{Mathematica} package \texttt{PolyLogTools}~\cite{Duhr:2019tlz}, which enables the computation of symbols of arbitrary combinations of GPLs. Indeed, with the help of this package, it is trivial to verify that the sum of symbols of the terms on the RHS is equal to Eq.~\ref{eq:Li3symbol}.

The \texttt{PolyLogTools} package introduces several powerful tools related to the symbol. In particular, we point out its functionality related to the so-called `fibration basis'. Given a GPL expression $F$ whose letters (i.e. the arguments) satisfy certain conditions, it is possible to write it in the following form:
\begin{equation}
    F = \sum_i c_i\, G(\vec{a}_i;\, x)\,,
\end{equation}
for some variable $x$, where $\vec{a}_i$ are independent of $x$ and the coefficients $c_i$ include only those GPLs that are independent of $x$ (see Ref.~\cite{Duhr:2019tlz} and references therein). The GPLs appearing on the RHS of this formula are known as the fibration basis. Moreover, it is also possible to `integrate' a symbol: given a symbol tensor $S$, it is possible to find a fibration basis such that $\SS(F) = S.$  This means that we can determine the functional form corresponding to a symbol expression (up to beyond-the-symbol terms). 
\section{Relation to canonical DEs and discontinuities}
Let us now take a step back and make a connection between the symbols and the differential equations satisfied by master integrals. In Section~\ref{sec:DEs}, we saw that by making a suitable change of basis, it is possible to construct MIs such that the corresponding DEs are in the canonical form of Eq.~\ref{eq:canonicalDEsoneform}. Then, their solution is given by a path-ordered exponential of the $\eps$-free DE matrix $\tilde{A}$. This exponential is understood through its series expansion, leading to repeated integrations over kernels dictated by $\tilde{A}$. Further, we introduced the notion of uniform transcendentality and an even stronger condition on `pure' functions, Eq.~\ref{eq:purecondition}, which says that the transcendental weight of pure functions is lowered by 1 upon differentiation. Moreover, we learned that the solution of any canonical DEs is pure and vice versa --- a given basis of pure functions will satisfy the canonical DEs. We should therefore be able to write down these DEs in a way which makes the purity property manifest. Indeed, notice that the differential equivalent of Eq.~\ref{eq:DEssolution} is:
\begin{equation}
    \dd \vv{\text{MI}}^{(k)} = \dd \tilde{A} \, \vv{\text{MI}}^{(k-1)} \quad \forall k>0, \qquad \dd \vv{\text{MI}}^{(0)} = 0\,.
\end{equation}
If we specialise to the cases where the DE matrix can be written in the $\dd \log$ form of Eq.~\ref{eq:dlogform}, then (for $k>0$) this becomes:
\begin{equation} \label{eq:pureMIDEs}
    \dd \vv{\text{MI}}^{(k)} = \left( \sum_i a_i \, \dd \log w_i  \right)\vv{\text{MI}}^{(k-1)}\,.
\end{equation}
Note that $\vv{\text{MI}}^{(0)}$ must be a vector of constants due to its vanishing derivative. This means that the leading term in the Laurent expansion of pure MIs does not contain any kinematic dependence. 

We can use Eq.~\ref{eq:pureMIDEs} to express the solution of the canonical DEs up to and including weight $n$ in the following form:
\begin{equation} \label{eq:pureMIDEsupton}
    \vv{\text{MI}}^{(n)} = \sum_{\alpha_1, \ldots, \alpha_n} \vec{c}_{\alpha_1, \ldots, \alpha_n} \int \dd \log w_{\alpha_1} \ldots \dd \log w_{\alpha_n}\,, \qquad n>0 \,.
\end{equation}
Note that each coefficient $\vec{c}_{\alpha_1, \ldots, \alpha_n}$ is a vector of rational numbers --- they are calculated from the products of matrices $a_i$, which are dotted into the weight-0 vector $\vv{\text{MI}}^{(0)}$. Naturally, to obtain explicit values for $\vv{\text{MI}}^{(n)}$, we need to supply the integration contour. Nonetheless, the symbol, which discards this information, can still tell us a lot about the analytic structure of the solution. It can be trivially read off from the above equation:
\begin{equation}
    \SS\left(\vv{\text{MI}}^{(n)}\right) = \sum_{\alpha_1, \ldots, \alpha_n} \vec{c}_{\alpha_1, \ldots, \alpha_n} [w_{\alpha_1}, \ldots, w_{\alpha_n}]\,.
\end{equation}
It turns out that the first entry of the symbol encodes its branch cut structure. In particular, a Feynman integral with the symbol $[w_{\alpha_1}, \ldots, w_{\alpha_n}]$ has a discontinuity if $w_{\alpha_1}=0$ or $\infty$. Of course, singular points of Feynman integrals are not random and we expect them to be connected to special values of the Mandelstam variables. Indeed, there exists a so-called first-entry condition which states that $\vec{c}_{\alpha_1, \ldots, \alpha_n}=0$ if $w_{\alpha_1} \neq s_{ij}$, i.e. a symbol cannot appear in the solution of the DEs if its first letter is not a Mandelstam variable with a physical discontinuity\footnote{Strictly speaking, it is the absence of discontinuities at certain points that implies the first-entry condition, but this statement should not be inverted. In fact, it is possible to write an amplitude using a function which satisfies the first-entry condition, yet has the forbidden singularity. See Section 3 of Ref.~\cite{Zoia:2021zmb} for an explicit example.}\cite{Gaiotto:2011dt}. This turns out to be a very strong condition which in many cases fixes the values of $\vv{\text{MI}}^{(0)}$ up to an overall normalisation factor. Beyond the first entry, the structure of the symbols is further constrained by the so-called Steinmann relations, which state that there is no double continuity associated with overlapping channels~\cite{20.500.11850/135473, Steinmann:1960, Caron-Huot:2016owq, Dixon:2016nkn}. Overall, such conditions created by physical principles constrain the structure of the symbols and canonical DEs. This is evident when studying the pure MI bases relevant to this thesis (see Refs.~\cite{Abreu:2020jxa, abreu2021twoloop}).
\renewcommand{\theequation}{C.\arabic{section}.\arabic{equation}}
\chapter{Derivation of the pole structure} \label{app:polestructure}
In this appendix, we provide a detailed derivation of the full pole structure of the $\ppbbh$ amplitudes presented in Eqs.~\ref{eq:poles1L} to \ref{eq:H2bbggH}. We do this for completeness, but also in the hope of illuminating the procedure, which can be far from obvious. The pole structure of the $\ppWgj$ amplitudes can be derived similarly. We also outline the related calculation for the $0\to \ell \bar\ell \gamma \gamma^*$ QED amplitudes of Chapter~\ref{sec:QEDpaper}.
\section{UV singularities}
Let us start with the UV singularities. Renormalising the amplitude amounts to replacing the bare couplings $x_B$ in the Lagrangian with the physical ones:
\begin{equation}
    x_B = Z_x x_R \,.
\end{equation}
The renormalisation factors are expanded as $Z_x = 1 + \delta_x$, where $\delta_x$ are the counterterms added to the bare Lagrangian and which are designed precisely to cancel out the divergences. Thus, we can think of renormalisation as absorbing the infinities from $x_B$ into $Z_x$. Then, working with the renormalised parameters $x_R$ in the Lagrangian is known as `renormalised perturbation theory'. Let us now see how to achieve that. Specialising to the $\ppbbh$ process of Chapter~\ref{sec:Hbb}, the bare amplitude admits the following expansion (similar to that of Eq.~\ref{eq:ampexpansion}):
\begin{equation} \label{eq:ampexpbare}
    A_B = a_B y_{b,B} \left(A_B^{(0)} + a_B A_B^{(1)} + a_B^2 A_B^{(2)} + \ldots \right)\,,
\end{equation}
where $a_B = \alpha_{s,B}/(4\pi)$ and $\alpha_{s,B}$, $y_{b,B}$ are the bare strong coupling constant and the bare Yukawa coupling of the $b$ quark\footnote{See Refs.~\cite{Ahmed:2014pka, Mondini:2019vub} for details, but note the difference of $\alpha_{s,B}^{1/2}$ as the leading power due to one fewer jet and, in the second reference, the expansion in powers of $\alpha_{s,B}/(2 \pi)$, which introduces relative factors of $2$ with respect to our convention.}. We will work in the $\overline{\text{MS}}$ scheme and make the following replacements for the two couplings\footnote{We treat all quarks as massless, while the wave function counterterm in the massless on-shell scheme is 0 (see Section~\ref{Hbbsec:amp} for an explanation as to why we use a mixed renormalisation scheme). Therefore, we only renormalise the strong coupling constant and the $b$ quark Yukawa coupling.}:
\begin{align}
    \alpha_{s,B} &= S_\eps\, Z_{\alpha_s} \, \alpha_{s,R}(\mu_R), \label{eq:baretorenormalpha} \\
    y_{b,B} &= Z_y \, y_{b,R}(\mu_R) \label{eq:baretorenormyb} \,,
\end{align}
where $\mu_R$ is the renormalisation scale. The factor $S_\eps = \mathrm{e}^{\eps \gamma_E} (4\pi)^{-\eps}$ cancels out with the $m_\eps$ factor extracted from the colour-ordered amplitudes in Eq.~\ref{eq:colourdecomposition} and so will be dropped in the following discussion. The renormalisation factors themselves admit a perturbative expansion in the renormalised strong coupling constant:
\begin{align}
    Z_{\alpha_s} &= 1 + a_R r_1 + a_R^2 r_2 + \order{a_R^3},  \label{eq:Zalphacoeff} \\
    Z_y &= 1 + a_R s_1 + a_R^2 s_2 + \order{a_R^3} \label{eq:Zybcoeff}\,,
\end{align}
where $a_R = \alpha_{s,R}/(4\pi)$. Substituting Eqs.~\ref{eq:baretorenormalpha} through \ref{eq:Zybcoeff} into Eq.~\ref{eq:ampexpbare}, we obtain the amplitude expansion in terms of the renormalised parameters:
\begin{equation} \label{eq:ampexprenorm}
    A_R = a_R y_{b,R} \left(A_R^{(0)} + a_R A_R^{(1)} + a_B^2 A_R^{(2)} + \ldots \right)\,,
\end{equation}
with the individual amplitudes given by:
\begin{align}
    A_R^{(0)} &= A_B^{(0)} \,,\nonumber \\ 
    A_R^{(1)} &= A_B^{(1)} + 2 A_B^{(0)}(r_1 + s_1) \,, \label{eq:amprenorminbare}\\ 
    A_R^{(2)} &= A_B^{(2)} + 2 A_B^{(1)}(2r_1 + s_1) + 4A_B^{(0)} (r_2 + r_1 s_1 + s_2)\,. \nonumber
\end{align}
The coefficients $r_1, r_2, s_1, s_2$ are listed in Appendix~\ref{app:renormconstants}. Note that we use their values as given in Ref.~\cite{Mondini:2019vub} for the sake of consistency, but in Eq.~\ref{eq:amprenorminbare} we have rescaled them by powers of 2 to make them compatible with our expansion. Overall, we see that each UV-finite amplitude $A_R^{(L)}$ is defined by adding to the bare amplitude $A_B^{(L)}$ terms related to the $\beta$-function whose $\eps$ poles cancel out the UV divergences. This completes the renormalisation of the $\ppbbh$ amplitudes in Chapter~\ref{sec:Hbb}.
\section{IR singularities}
The renormalised amplitudes $A_R^{(L)}$ are only UV-finite --- the IR divergences remain. The IR pole structure of two-loop amplitudes in massless gauge theories was originally derived in Ref.~\cite{Catani:1998bh} and later extended in  Refs.~\cite{Becher:2009cu, Becher:2009qa, Gardi:2009qi}. Here, we provide a brief summary of these results, followed by their application to our process of interest, $\ppbbh$.
\subsection{Overview of IR singularities}
The $\overline{\text{MS}}$-renormalised amplitudes $A_R^{(L)}$ admit the following structure\footnote{Note that similarly to the previous section, we rescale $\bm{I}^{(1)}(\eps)$ and $\bm{I}^{(2)}(\eps)$ by $2$ and $2^2$, respectively, to account for the different expansion parameter $a_R$ in Ref.~\cite{Catani:1998bh}.}:
\begin{align}
    A_R^{(1)} &= 2\bm{I}^{(1)}(\eps) A_R^{(0)} + F^{(1)}\,, \label{eq:A1IRstructure} \\
    A_R^{(2)} &= 2\bm{I}^{(1)}(\eps) A_R^{(1)} + 4\bm{I}^{(2)}(\eps) A_R^{(0)} + F^{(2)} \,. \label{eq:A2IRstructure}
\end{align}
The IR-divergent part is determined by amplitudes at lower loop order, while the full amplitude also receives a finite part $F^{(L)}$, which is the genuinely new contribution that needs to be computed. The pole operators $\bm{I}^{(L)}(\eps)$ are given by~\cite{Catani:1998bh}:
\begin{align}
    \bm{I}^{(1)}(\eps) &= \frac{1}{2} \frac{\mathrm{e}^{\eps \gamma_E}}{\Gamma(1-\eps)} \sum_i \left(\frac{1}{\eps^2} - \frac{\gamma_0^i}{2\eps} \frac{1}{\bm{T}_i^2}\right) \sum_{j\neq i} \bm{T}_j \cdot \bm{T}_j \left(\frac{\mu_R^2}{-s_{ij}} \right)^\eps\,, \\
    \bm{I}^{(2)}(\eps) &= \frac{\mathrm{e}^{-\eps \gamma_E} \Gamma(1-2\eps)}{\Gamma(1-\eps)} \left( \frac{\gamma_1^\text{cusp}}{8} + \frac{\beta_0}{2\eps} \right) \bm{I}^{(1)}(2\eps) - \frac{1}{2}\bm{I}^{(1)}(\eps) \left(\bm{I}^{(1)}(\eps) + \frac{\beta_0}{\eps} \right) + \bm{H}_{\text{RS}}^{(2)}(\eps)\,,
\end{align}
where $s_{ij} = 2 \sigma_{ij} \, p_i \cdot p_j$ with $\sigma_{ij}=+1$ if both momenta are incoming or outgoing and $\sigma_{ij}=-1$ otherwise. The values of the $\beta$-function coefficients and the anomalous dimensions are given in Appendix~\ref{app:renormconstants}. We remark that the one-loop pole operator $\bm{I}^{(1)}(\eps)$ is independent of the regularisation scheme, while the two-loop operator $\bm{I}^{(2)}(\eps)$ is not. Its dependence enters through the quantity $\bm{H}_{\text{RS}}^{(2)}(\eps)$, which contains $\order{1/\eps}$ poles only:
\begin{align} \label{eq:IR_H_function}
    \bm{H}_{\text{RS}}^{(2)}(\eps) &= \frac{1}{16\eps} \sum_i \left(\gamma_1^i - \frac{1}{4} \gamma_1^{\text{cusp}}\gamma_0^i + \frac{\pi^2}{16} \beta_0 \gamma_0^{\text{cusp}} C_i \right) \nonumber \\
    &+ \frac{\ii f^{abc}}{24\eps} \sum_{(i,j,k)} \bm{T}_i^a \bm{T}_j^b \bm{T}_k^c \ln\left(\frac{-s_{ij}}{-s_{jk}} \right) \ln\left(\frac{-s_{jk}}{-s_{ki}} \right) \ln\left(\frac{-s_{ki}}{-s_{ij}} \right) \\ 
    &-\frac{\ii f^{abc}}{128\eps} \gamma_0^{\text{cusp}} \sum_{(i,j,k)} \bm{T}_i^a \bm{T}_j^b \bm{T}_k^c \left( \frac{\gamma_0^i}{C_i} - \frac{\gamma_0^j}{C_j} \right)\ln\left(\frac{-s_{ij}}{-s_{jk}} \right) \ln\left(\frac{-s_{ki}}{-s_{ij}} \right)\,, \nonumber
\end{align}
where the sum runs over unordered tuples $(i,j,k)$ of distinct parton indices. As pointed out in Ref.~\cite{Becher:2009cu}, the last two lines appear only because the pole operators $\bm{I}^{(L)}(\eps)$ in Ref.~\cite{Catani:1998bh} were not defined in a minimal scheme, but also include terms finite in $\eps$. Due to colour conservation, they contribute only if the amplitude contains at least four partons. Additionally, the last line appears only for \textit{more} than 4 partons due to momentum conservation. More importantly, these last two lines produce terms subleading in $N_c$. Thus, in the leading-colour approximation, we will neglect them and use the first line only.

Overall, despite the intimidating appearance of the formulas above, it can be appreciated that the only non-trivial piece of deriving the IR pole structure of the two-loop amplitudes is due to the operators $\bm{T}_i^a$, which we will refer to as `colour insertion operators'. Each $\bm{T}_i^a$ acts on the colour structure of the amplitude by inserting a gluon with the adjoint index $a$ onto the parton $i$. The rules are as follows:
\begin{itemize}
    \item $\bm{T}_c^a: \delta^{bc} = -\ii f^{abc}$ if $c$ is a gluon,
    \item $\bm{T}_i^a: \delta_{ij} = + (T^a)_{ij}$ if $i$ is an outgoing quark,
    \item $\bm{T}_i^a: \delta_{ji} = - (T^a)_{ji}$ if $i$ is an outgoing antiquark,
    \item $\bm{T}_i^a: \delta_{ji} = - (T^a)_{ji}$ if $i$ is an incoming quark,
    \item $\bm{T}_i^a: \delta_{ij} = + (T^a)_{ij}$ if $i$ is an incoming antiquark.
\end{itemize}
We find it very helpful to use pictures akin to Feynman diagrams to better understand these rules (see  Fig.~\ref{fig:colourinsertion}). 
\begin{figure}
    \centering
    %\begin{adjustbox}{minipage=\textwidth,scale=0.9}
    %\raisebox{0.2cm}{
    \begin{subfigure}[b]{0.8\linewidth}
        \hspace*{1em}
        \begin{tikzpicture}[every text node part/.style={align=left}]
    	\begin{feynman}[small]
    		\vertex (v) node[anchor=north] {$b$};
            \vertex (f) [right=2cm of v] {$\phantom{i_1}$};
            \node at (f.south west) {$c$};
            \node (t) [left=0.5cm of v] {$\bm{T}^a_c:$};
            \node (eq) [right=0.5cm of f] {$=$};

            \vertex (v2) [right=0.5cm of eq] {$-\ii$};
            \node at (v2.south east) {$b$};
            \vertex (m) [right=1.3cm of v2] [anchor=west];
            \vertex (f2) [right=1.2cm of m] {\phantom{j}};
            \node at (f2.south west) {$c$};
            \vertex (g) [above=of m] {$a$};

            \node (text) [right=1.7cm of f2] {gluon};
            
    		\diagram*{
    			(v) -- [thick, gluon] (f);
                (v2) -- [thick, gluon] (m) -- [thick, gluon] (f2);
                (m) -- [thick, gluon] (g);
    		};
    	\end{feynman}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{0.8\linewidth}
        \hspace*{1em}
        \begin{tikzpicture}[every text node part/.style={align=left}]
    	\begin{feynman}[small]
    		\vertex (v) node[anchor=north] {$j$};
            \vertex (f) [right=2cm of v] {$\phantom{i_1}$};
            \node at (f.south west) {$i$};
            \node (t) [left=0.5cm of v] {$\bm{T}^a_i:$};
            \node (eq) [right=0.5cm of f] {$=$};

            \vertex (v2) [right=0.5cm of eq] {$+$};
            \node at (v2.south east) {$j$};
            \vertex (m) [right=1.3cm of v2] [anchor=west];
            \vertex (f2) [right=1.2cm of m] {\phantom{j}};
            \node at (f2.south west) {$i$};
            \vertex (g) [above=of m] {$a$};

            \node (text) [right=2cm of f2] {outgoing\\quark};
            
            \filldraw (v) circle (2pt);
            \filldraw (v2.east) circle (2pt);
            
    		\diagram*{
    			(v) -- [thick, fermion] (f);
                (v2) -- [thick, fermion] (m) -- [thick, fermion] (f2);
                (m) -- [thick, gluon] (g);
    		};
    	\end{feynman}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{0.8\linewidth}
        \hspace*{1em}
        \begin{tikzpicture}[every text node part/.style={align=left}]
    	\begin{feynman}[small]
    		\vertex (v) node[anchor=north] {$j$};
            \vertex (f) [right=2cm of v] {$\phantom{i_1}$};
            \node at (f.south west) {$i$};
            \node (t) [left=0.5cm of v] {$\bm{T}^a_i:$};
            \node (eq) [right=0.5cm of f] {$=$};

            \vertex (v2) [right=0.5cm of eq] {$-$};
            \node (c) at (v2.south east) {$j$};
            \vertex (m) [right=1.3cm of v2] [anchor=west];
            \vertex (f2) [right=1.2cm of m] {\phantom{j}};
            \node at (f2.south west) {$i$};
            \vertex (g) [above=of m] {$a$};

            \node (text) [right=2cm of f2] {outgoing\\antiquark};
            
            \filldraw (v) circle (2pt);
            \filldraw (v2.east) circle (2pt);
            
    		\diagram*{
    			(v) -- [thick, anti fermion] (f);
                (v2) -- [thick, anti fermion] (m) -- [thick, anti fermion] (f2);
                (m) -- [thick, gluon] (g);
    		};
    	\end{feynman}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{0.8\linewidth}
        \hspace*{1em}
        \begin{tikzpicture}[every text node part/.style={align=left}]
    	\begin{feynman}[small]
    		\vertex (v) node[anchor=north] {$i$};
            \vertex (f) [right=2cm of v] {$\phantom{i_1}$};
            \node at (f.south west) {$j$};
            \node (t) [left=0.5cm of v] {$\bm{T}^a_i:$};
            \node (eq) [right=0.5cm of f] {$=$};

            \vertex (v2) [right=0.5cm of eq] {$-$};
            \node at (v2.south east) {$i$};
            \vertex (m) [right=1.3cm of v2] [anchor=west];
            \vertex (f2) [right=1.2cm of m] {\phantom{j}};
            \node at (f2.south west) {$j$};
            \vertex (g) [above=of m] {$a$};

            \node (text) [right=2cm of f2] {incoming\\quark};
            
            \filldraw (f.west) circle (2pt);
            \filldraw (f2.west) circle (2pt);
            
    		\diagram*{
    			(v) -- [thick, fermion] (f);
                (v2) -- [thick, fermion] (m) -- [thick, fermion] (f2);
                (m) -- [thick, gluon] (g);
    		};
    	\end{feynman}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{0.8\linewidth}
        \hspace*{1em}
        \begin{tikzpicture}[every text node part/.style={align=left}]
    	\begin{feynman}[small]
    		\vertex (v) node[anchor=north] {$i$};
            \vertex (f) [right=2cm of v] {$\phantom{i_1}$};
            \node at (f.south west) {$j$};
            \node (t) [left=0.5cm of v] {$\bm{T}^a_i:$};
            \node (eq) [right=0.5cm of f] {$=$};

            \vertex (v2) [right=0.5cm of eq] {$+$};
            \node at (v2.south east) {$i$};
            \vertex (m) [right=1.3cm of v2] [anchor=west];
            \vertex (f2) [right=1.2cm of m] {\phantom{j}};
            \node at (f2.south west) {$j$};
            \vertex (g) [above=of m] {$a$};

            \node (text) [right=2cm of f2] {incoming\\antiquark};
            
            \filldraw (f.west) circle (2pt);
            \filldraw (f2.west) circle (2pt);
            
    		\diagram*{
    			(v) -- [thick, anti fermion] (f);
                (v2) -- [thick, anti fermion] (m) -- [thick, anti fermion] (f2);
                (m) -- [thick, gluon] (g);
    		};
    	\end{feynman}
    \end{tikzpicture}
    \end{subfigure}
    %}
    %\end{adjustbox}
\caption{Graphical representation of the action of the colour insertion operators on partons. The dot $\bullet$ indicates a Feynman diagram vertex and allows us to distinguish between incoming and outgoing quarks and antiquarks. The fundamental and antifundamental indices should be read in the direction opposite to fermion flow, while the adjoint indices in the three-point gluon vertex should be read anticlockwise.}
\label{fig:colourinsertion}
\end{figure}
Before applying them to our process of interest, it is useful to note that the product of two colour insertion operators, $\bm{T}_i\cdot\bm{T}_j \equiv \bm{T}_i^a \bm{T}_j^a$, trivially commutes: 
\begin{equation} \label{eq:TiTjcommute}
    \bm{T}_i\cdot\bm{T}_j = \bm{T}_j\cdot\bm{T}_i\,,
\end{equation}
while for $i=j$ the action of the product gives the quadratic Casimir of the appropriate representation of $SU(N_c)$:
\begin{equation} \label{eq:Ti^2eqCi}
    \bm{T}_i^2 = C_i\,,
\end{equation}
with $C_q = C_{\bar{q}} = C_F$ and $C_g=C_A$. Moreover, due to colour conservation:
\begin{align} 
    \sum_{i=1}^n \bm{T}_i^a \ket{A_n} &= 0\,, \label{eq:poleinsertioncheckA} \\
    \sum_{(i,j)} \bm{T}_i \cdot \bm{T}_j = -\sum_i \bm{T}_i^2 &= -\sum_i C_i\,, \label{eq:poleinsertioncheckB}
\end{align}
where $\ket{A_n}$ denotes a vector in the $n$-dimensional colour space, with $A_n$ being the UV-renormalised amplitude of $n$ coloured partons\footnote{For a description of the colour-space formalism, see Ref.~\cite{Catani:1996vz}.}. These equations can be used to check whether we have applied the colour insertion operators to our amplitude correctly.
\subsection{Application to $\ppbbh$ amplitudes}
We now have all the tools to derive the IR pole structure of the $\ppbbh$ amplitudes in Chapter~\ref{sec:Hbb}. First of all, we note that by applying the first line of Eq.~\ref{eq:IR_H_function} to the $\bbqqh$ and $\bbggh$ channels, Eqs.~\ref{eq:H2bbqqH} and \ref{eq:H2bbggH} follow trivially. Then, to derive the two-loop pole operator $\bm{I}^{(2)}(\eps)$, we only need to concern ourselves with the action of the colour insertion operators $\bm{T}_i^a$ within $\bm{I}^{(1)}(\eps)$.
\subsubsection{The $\bbqqh$ channel}
As the first step, we write down all the colour structures that appear in the relevant Feynman diagrams. Note that factors such as $N_c, T_F, C_A$ or $C_F$ are not considered a part of these structures --- we only include $\delta$-functions, fundamental generators $(T^a)_i^{\;\;\bar{j}}$ and the structure constants $f^{abc}$. For this channel, we find two colour structures (see Fig.~\ref{fig:bbqqHcolour}):
\begin{equation}
    \bm{c} = 
    \begin{pmatrix}
        \delta_{i_4}^{\;\;\bar{i}_1} \delta_{i_2}^{\;\;\bar{i}_3} & \quad \delta_{i_2}^{\;\;\bar{i}_1} \delta_{i_4}^{\;\;\bar{i}_3}
    \end{pmatrix}^T\,.
\end{equation}
Then, the action of the products $\bm{T}_i \cdot \bm{T}_j$ produces linear combinations of these structures, which we encode in the matrices $\mathcal{C}_{ij}$ defined as follows:
\begin{equation}
    \bm{T}_i \cdot \bm{T}_j :  \bm{c} = \mathcal{C}_{ij} \bm{c}\,.
\end{equation}
Note that we do not have to compute $\mathcal{C}_{ij}$ for all possible combinations of partons $i$ and $j$. Due to Eq.~\ref{eq:Ti^2eqCi}, all $\mathcal{C}_{ii}$ are diagonal and their entries are given by the quadratic Casimirs $C_i$ in the relevant representation. Moreover, the commutativity property Eq.~\ref{eq:TiTjcommute} further reduces the number of necessary computations. Overall, for $n$ coloured partons, we only need to compute $n(n+1)/2$ matrices.
\begin{figure}
    \centering
        \begin{tikzpicture}
        	\begin{feynman}[small]
        		\vertex (v1);
          
        		\vertex[above left = 1cm of v1] (i1) {$i_4$};
        		\vertex[below left =  1cm of v1] (i2) {$\bar{i}_3$};
        		\vertex[right = of v1] (v2);			
        		
        		\vertex[above right = 1cm of v2] (f1) {$\bar{i}_1$};
        		\vertex[below right = 1cm of v2] (f2) {$i_2$};

                %2nd diagram
                \vertex[below right=of f1, xshift=1.5cm] (2i1) {$i_4$};
                \vertex[above right=of f2, xshift=1.5cm] (2i2) {$\bar{i}_3$};
                		
        		\vertex[right=2cm of 2i1] (2f1) {$\bar{i}_1$};
                \vertex[right=2cm of 2i2] (2f2) {$i_2$}; 

                %3rd diagram
                \vertex[above right=of 2f1, xshift=1cm] (3i1) {$i_4$};
                \vertex[below right=of 2f2, xshift=1cm] (3i2) {$\bar{i}_3$};
                		
        		\vertex[right=of 3i1] (3f1) {$\bar{i}_1$};
                \vertex[right=of 3i2] (3f2) {$i_2$}; 

                %equation nodes
                \node[right=2.5cm of v1] {$=T_F$ \Huge $\Biggr($};
                \node[right=6.5cm of v1] {$ -\,\,\dfrac{1}{N_c} $};
                \node[right=9cm of v1] {\Huge $\Biggr)$};

        		\diagram*{
                    %1st diagram
        			(i1) -- [anti fermion] (v1) -- [anti fermion] (i2),
                    (v1) -- [gluon] (v2),
        			(f1) -- [fermion] (v2) -- [fermion] (f2),
                    %2nd diagram
                    (2i1) -- [anti fermion] (2f1),
                    (2i2) -- [fermion] (2f2),
                    %3rd diagram
                    (3i1) -- [anti fermion] (3i2),
                    (3f1) -- [fermion] (3f2),
        		};
        	\end{feynman}
        \end{tikzpicture}
    \caption{The colour structure of a sample diagram contributing to the $\bbqqh$ channel at tree level. We employ the Fierz identity to write $(T^a)_{i_4}^{\;\;\bar{i}_3} (T^a)_{i_2}^{\;\;\bar{i}_1} = T_F \left( \delta_{i_4}^{\;\;\bar{i}_1} \delta_{i_2}^{\;\;\bar{i}_3} - \frac{1}{N_c} \delta_{i_2}^{\;\;\bar{i}_1} \delta_{i_4}^{\;\;\bar{i}_3}\right)$. Note that particles 3 and 4 have to be crossed into the final state to correspond to the process definition in Eq.~\ref{eq:subprocessqq}, where all particles are outgoing. Thus, we should treat them as an outgoing antiquark and an outgoing quark, respectively, when applying the rules from Fig.~\ref{fig:colourinsertion}.} 
    \label{fig:bbqqHcolour}
\end{figure}

As an example, let us see how the operator product $\bm{T}_1 \cdot \bm{T}_4$ acts on the two colour structures in this channel. Applying the rules listed in Fig.~\ref{fig:colourinsertion} (remember that particle 3 is treated as an outgoing antiquark, while particle 4 as an outgoing quark):
\begin{align}
    \bm{T}_1 \cdot \bm{T}_4 : \delta_{i_4}^{\;\;\bar{i}_1} \delta_{i_2}^{\;\;\bar{i}_3} &= -(T^a T^a)_{i_4}^{\;\;\bar{i}_1} \delta_{i_2}^{\;\;\bar{i}_3} = -C_F \delta_{i_4}^{\;\;\bar{i}_1} \delta_{i_2}^{\;\;\bar{i}_3}\,, \\
    \bm{T}_1 \cdot \bm{T}_4 : \delta_{i_2}^{\;\;\bar{i}_1} \delta_{i_4}^{\;\;\bar{i}_3} &= -(T^a)_{i_2}^{\;\;\bar{i}_1} (T^a)_{i_4}^{\;\;\bar{i}_3} = -T_F \left(\delta_{i_4}^{\;\;\bar{i}_1}\delta_{i_2}^{\;\;\bar{i}_3} - \frac{1}{N_c}\delta_{i_2}^{\;\;\bar{i}_1} \delta_{i_4}^{\;\;\bar{i}_3} \right) \,,
\end{align}
where in both lines we have used the Fierz identity in the last equality. Perhaps a graphical representation of these operations in Fig.~\ref{fig:qqinsertion} is once again more illustrative. We can now read off the matrix $\mathcal{C}_{14}$:
\begin{equation}
    \mathcal{C}_{14} = 
    \begin{pmatrix}
    -C_F & 0 \\
    -T_F & \frac{T_F}{N_c}
\end{pmatrix}\,.
\end{equation}
In the same manner, we need to obtain the remaining matrices $\mathcal{C}_{ij}$. Needless to say, performing these operations by hand (or even using their diagrammatical equivalents) becomes tedious and extremely prone to errors. We therefore automate this task in \texttt{Mathematica} and make use of the package \texttt{ColorMath}~\cite{Sjodahl:2012nk} to achieve the simplifications of the various colour structures that arise as a result of applying the colour insertion operators. We make sure to verify that Eq.~\ref{eq:poleinsertioncheckB} holds as a check on our calculations.
\begin{figure}
    \centering
    \begin{subfigure}{\linewidth}
        \begin{tikzpicture}
        	\begin{feynman}[small]
        		\vertex (i1) {$i_4$};
        		\vertex[right =3cm of i1] (f1) {$\bar{i}_1$};
        		\vertex[below =0.7cm of i1] (i2) {$\bar{i}_3$};
        		\vertex[right =3cm of i2] (f2) {$i_2$};			
        		
                %2nd diagram
                \vertex[right=of f1, xshift=0.8cm] (2i1) {$i_4$};
                \vertex[right=of f2, xshift=0.8cm] (2i2) {$\bar{i}_3$};
                		
        		\vertex[right=of 2i1] (2m1);
                \vertex[right=of 2m1] (2m2);
                
        		\vertex[right=of 2m2] (2f1) {$\bar{i}_1$};
                \vertex[below=0.7cm of 2f1] (2f2) {$i_2$}; 

                %3rd diagram
                \vertex[right=of 2f1, xshift=1cm] (3i1) {$i_4$};
                \vertex[right=of 2f2, xshift=1cm] (3i2) {$\bar{i}_3$};
                \vertex[right=3cm of 3i1] (3f1) {$\bar{i}_1$};
                \vertex[below=0.7cm of 3f1] (3f2) {$i_2$}; 
                
                %equation nodes
                \node (t1) [left=1.2cm of i1, yshift=-0.35cm] {$\bm{T}_1 \cdot \bm{T}_4:$};
                \node (t2) [right=5cm of t1] {$\;\;=\;\;-$};
                \node (t3) [right=5.3cm of t2] {$= \;\;-C_F$};

        		\diagram*{
                    %1st diagram
        			(i1) -- [anti fermion] (f1),
                    (i2) -- [fermion] (f2),
                    %2nd diagram
                    (2i1) -- (2m1) -- [anti fermion] (2m2) -- (2f1),
                    (2i2) -- [fermion] (2f2),
                    (2m1) -- [gluon, out=90, in=90] (2m2),
                    %3rd diagram
        			(3i1) -- [anti fermion] (3f1),
                    (3i2) -- [fermion] (3f2),
        		};
        	\end{feynman}
        \end{tikzpicture}
    \caption{}
    %\label{}
    \end{subfigure}
    \begin{subfigure}{\linewidth}
    \vspace{0.5cm}
        \begin{tikzpicture}
        	\begin{feynman}[small]
        		\vertex (i1) {$i_4$};
        		\vertex[below=2.3cm of i1] (i2) {$\bar{i}_3$};
                \vertex[right=of i1] (f1) {$\bar{i}_1$};
                \vertex[below=2.3cm of f1] (f2) {$i_2$};

                %2nd diagram
                \vertex[right=of f1, xshift=0.5cm] (2i1) {$i_4$};
                \vertex[below=of 2i1] (2im);
                \vertex[below=of 2im] (2i2) {$\bar{i}_3$};
                		
        		\vertex[right=of 2i1] (2f1) {$\bar{i}_1$};
        		\vertex[below=of 2f1] (2fm);
                \vertex[right=of 2i2] (2f2) {$i_2$}; 

                %3rd diagram
                \vertex[right=2.5cm of 2f1, yshift=-0.6cm] (3i1) {$i_4$};
        		\vertex[right =2cm of 3i1] (3f1) {$\bar{i}_1$};
        		\vertex[right=2.5cm of 2f2, yshift=0.8cm] (3i2) {$\bar{i}_3$};
        		\vertex[right =2cm of 3i2] (3f2) {$i_2$};

                %4th diagram
                \vertex[above right=of 3f1, xshift=1cm] (4i1) {$i_4$};
                \vertex[below right=of 3f2, xshift=1cm] (4i2) {$\bar{i}_3$};
                		
        		\vertex[right=of 4i1] (4f1) {$\bar{i}_1$};
                \vertex[right=of 4i2] (4f2) {$i_2$}; 

                %equation nodes
                \node (t1) [below left=1.5cm of i1, xshift=-0.2cm] {$\bm{T}_1 \cdot \bm{T}_4:$};
                \node (t2) [right=3cm of t1] {$\;\;=\;\;-$};
                \node (t3) [right=3cm of t2] {$= \;\;-T_F$ \Huge $\Biggr($};
                \node (t4) [right=4.2cm of t3] {$ -\,\,\dfrac{1}{N_c} $};
                \node (t5) [right=2.2cm of t4] {\Huge $\Biggr)$};

        		\diagram*{
                    %1st diagram
        			(i1) -- [anti fermion] (i2),
        			(f1) -- [fermion] (f2),
                    %2nd diagram
        			(2i1) -- [anti fermion] (2im) -- [anti fermion] (2i2),
        			(2f1) -- [fermion] (2fm) -- [fermion] (2f2),
                    (2im) -- [gluon] (2fm),
                    %3rd diagram
                    (3i1) -- [anti fermion] (3f1),
                    (3i2) -- [fermion] (3f2),
                    %4th diagram
                    (4i1) -- [anti fermion] (4i2),
                    (4f1) -- [fermion] (4f2),
        		};
        	\end{feynman}
        \end{tikzpicture}
    \caption{}
    %\label{}
    \end{subfigure}
    \caption{A pictorial representation of the action of the colour insertion operators $\bm{T}_1 \cdot \bm{T}_4$ on the colour factors (a): $\delta_{i_4}^{\;\;\bar{i}_1} \delta_{i_2}^{\;\;\bar{i}_3}$ and (b): $\delta_{i_2}^{\;\;\bar{i}_1} \delta_{i_4}^{\;\;\bar{i}_3}\,.$} 
    \label{fig:qqinsertion}
\end{figure}

Once all the matrices $\mathcal{C}_{ij}$ have been computed, we have all the information needed to act with the pole operators $\bm{I}^{(L)}$ on the renormalised amplitudes $A_R^{(L)}$ and subtract the IR singularities. Note that if we want to retain full colour dependence, for each colour-ordered amplitude the subtraction will involve multiple lower-loop amplitudes with different colour factors. However, within the leading-colour approximation the situation is much simpler as the pole operators become diagonal. Indeed, replacing each $\bm{T}_i \cdot \bm{T}_j$ with the corresponding $\mathcal{C}_{ij}$ (and each $\bm{T}_i^2$ with the corresponding quadratic Casimir $C_i$), we retain only the highest power of $N_c$ to find:
\begin{equation}
    \bm{I}_{\bbqqh}^{(1)} = -N_c \frac{N(\eps)}{2}\left(\frac{1}{\eps^2} + \frac{3}{2\eps} \right) \left((-s_{23})^{-\eps} + (-s_{14})^{-\eps}\right)
    \begin{pmatrix}
        1 & 0 \\
        0 & 1
    \end{pmatrix},
\end{equation}
where $N(\eps) = {\mathrm{e}^{\eps \gamma_E}}/{\Gamma(1-\eps)}$. Moreover, it turns out that the second colour factor $\delta_{i_2}^{\;\;\bar{i}_1} \delta_{i_4}^{\;\;\bar{i}_3}$ always appears suppressed by $1/N_c$ with respect to the first factor $\delta_{i_4}^{\;\;\bar{i}_1} \delta_{i_2}^{\;\;\bar{i}_3}$, as can be appreciated from our simple example in Fig.~\ref{fig:bbqqHcolour}. Thus, in the leading-colour approximation, we simply drop it. This justifies the decomposition in Eq.~\ref{eq:colourdecomposition} and completes the derivation of the pole operator $I_{\bbqqh}^{(1)}$ in Eq.~\ref{eq:I1bbqqh}, which now acts solely on the amplitude associated with the colour factor $\delta_{i_4}^{\;\;\bar{i}_1} \delta_{i_2}^{\;\;\bar{i}_3}$.

Finally, we combine the UV and IR poles in a single operator $P^{(L)}$ which we can use to subtract both types of divergences from the amplitude. Substituting Eq.~\ref{eq:amprenorminbare} into Eqs.~\ref{eq:A1IRstructure} and \ref{eq:A2IRstructure}, we obtain the finite part:
\hspace{-9.2cm}
\begin{minipage}[t]{16cm}
\begin{align}
    F^{(1)} &= A_R^{(1)} - 2 I^{(1)}(\eps) A_R^{(0)} \nonumber \\
            &= A_B^{(1)} + 2 A_B^{(0)}(r_1 + s_1) - 2 I^{(1)}(\eps) A_B^{(0)} \nonumber \\
            &= A_B^{(1)} - \underbrace{2 \left(I^{(1)}(\eps) - r_1 - s_1 \right)}_{P^{(1)}} A_B^{(0)} \,, \\
            &\nonumber \\
    F^{(2)} &= A_R^{(2)} - 2 I^{(1)}(\eps) A_R^{(1)} - 4 I^{(2)}(\eps) A_R^{(0)} \nonumber \\
            &= A_B^{(2)} + 2 A_B^{(1)}(2r_1 + s_1) + 4A_B^{(0)} (r_2 + r_1 s_1 + s_2) \nonumber \\
            & \quad \, -2 I^{(1)}(\eps) \left(A_B^{(1)} + 2 A_B^{(0)}(r_1 + s_1)\right) - 4 I^{(2)}(\eps) A_B^{(0)} \nonumber \\
            &= A_B^{(2)} - \underbrace{\big(2 I^{(1)}(\eps) \big(\hat{A}_B^{(1)} + 2 r_1 + 2 s_1\big) +4I^{(2)}(\eps) -2 (2r_1 + s_1) \hat{A}_B^{(1)} -  4(r_2 + r_1 s_1 + s_2) \big)}_{P^{(2)}} A_B^{(0)}\,,
\end{align}
\end{minipage}
%\begin{align}
%    F^{(1)} &= A_R^{(1)} - 2 I^{(1)}(\eps) A_R^{(0)} \nonumber \\
%            &= A_B^{(1)} + 2 A_B^{(0)}(r_1 + s_1) - 2 I^{(1)}(\eps) A_B^{(0)} \nonumber \\
%            &= A_B^{(1)} - \underbrace{2 \left(I^{(1)}(\eps) - r_1 - s_1 \right)}_{P^{(1)}} A_B^{(0)} \,, \\
%            &\nonumber \\
%    F^{(2)} &= A_R^{(2)} - 2 I^{(1)}(\eps) A_R^{(1)} - 4 I^{(2)}(\eps) A_R^{(0)} \nonumber \\
%            &= A_B^{(2)} + 2 A_B^{(1)}(2r_1 + s_1) + 4A_B^{(0)} (r_2 + r_1 s_1 + s_2) \nonumber \\
%            & -2 I^{(1)}(\eps) \left(A_B^{(1)} + 2 A_B^{(0)}(r_1 + s_1)\right) - 4 I^{(2)}(\eps) A_B^{(0)} \nonumber \\
%            &= A_B^{(2)} - \big(2 I^{(1)}(\eps) \big(\hat{A}_B^{(1)} + 2 r_1 + 2 s_1\big) +4I^{(2)}(\eps) \nonumber  \\
%            &\phantom{=A_B^{(2)}-(} \underbrace{\quad \qquad -2 (2r_1 + s_1) \hat{A}_B^{(1)} -  4(r_2 + r_1 s_1 + s_2) \big)}_{P^{(2)}} A_B^{(0)}\,,
%\end{align}
where $\hat{A}_B^{(1)}$ is the one-loop bare amplitude divided by the tree-level amplitude. Thus, to obtain the finite remainders, we simply subtract the operators $P^{(1)}$ and $P^{(2)}$ (multiplied by the tree-level amplitude) from the \textit{bare} amplitudes $A^{(1)}_B$ and $A^{(2)}_B$.
\subsubsection{The $\bbggh$ channel}
The derivation of the pole structure in the $\bbggh$ channel follows exactly the same steps as described in the previous section. However, we believe it is still useful to outline it, since there are a few subtleties that we did not have to take care of in the case of the $\bbggh$ channel. First of all, here we find three colour structures:
\begin{equation}
    \bm{c} = 
    \begin{pmatrix}
        (T^{a_3}T^{a_4})_{i_2}^{\;\;\bar{i}_1} & \quad (T^{a_4}T^{a_3})_{i_2}^{\;\;\bar{i}_1}
        & \quad \delta_{i_2}^{\;\;\bar{i}_1} \delta^{ab}
    \end{pmatrix}^T\,.
\end{equation}
While the first two factors can be spotted in a naive analysis of tree-level diagrams such as Fig.~\ref{fig:bbggHcolour}, the third factor appears only at loop level. Thus, from a practical point of view, it is useful to have an automated routine which is able to extract the colour structure of all diagrams up to the desired loop order.
\begin{figure}
    \centering
        \begin{tikzpicture}
        	\begin{feynman}[small]
        		\vertex (v1);
          
        		\vertex[above left = 1cm of v1] (i1) {$a_4$};
        		\vertex[below left =  1cm of v1] (i2) {$a_3$};
        		\vertex[right = of v1] (v2);			
        		
        		\vertex[above right = 1cm of v2] (f1) {$\bar{i}_1$};
        		\vertex[below right = 1cm of v2] (f2) {$i_2$};

                %2nd diagram
                \vertex[below right=of f1, xshift=1cm] (2i1) {$a_4$};
                \vertex[above right=of f2, xshift=1cm] (2i2) {$a_3$};
                		
        		\vertex[right=2cm of 2i1] (2f2);
        		\vertex[above=0.5cm of 2f2] (2f1) {$\bar{i}_1$};
                \vertex[right=2cm of 2i2] (2f3); 
                \vertex[below=0.5cm of 2f3] (2f4) {$i_2$}; 

                %3rd diagram
                \vertex[right=1.2cm of 2f2, ] (3i1) {$a_4$};
                \vertex[right=1.2cm of 2f3, ] (3i2) {$a_3$};
                		
        		\vertex[right=2cm of 3i1] (3f2);
        		\vertex[above=0.5cm of 3f2] (3f1) {$\bar{i}_1$};
                \vertex[right=2cm of 3i2] (3f3); 
                \vertex[below=0.5cm of 3f3] (3f4) {$i_2$}; 
                
                \node (t1) [right=1.2cm of v2] {$\;\;=\;\;$};
                \node (t2) [right=3.7cm of t1] {$-$};

        		\diagram*{
                    %1st diagram
        			(i1) -- [gluon] (v1) -- [gluon] (i2),
                    (v1) -- [gluon] (v2),
        			(f1) -- [fermion] (v2) -- [fermion] (f2),
                    %2nd diagram
                    (2f1) -- [fermion] (2f2) -- [fermion] (2f3) -- [fermion] (2f4);
                    (2i1) -- [gluon] (2f2),
                    (2i2) -- [gluon] (2f3),
                    %3rd diagram
                    (3f1) -- [fermion] (3f2) -- [fermion] (3f3) -- [fermion] (3f4);
                    (3i1) -- [gluon] (3f3),
                    (3i2) -- [gluon] (3f2),
        		};
        	\end{feynman}
        \end{tikzpicture}
    \caption{The colour structure of a sample diagram contributing to the $\bbggh$ channel at tree level. It is also a graphical representation of the relation which defines the structure constants, $\ii f^{abc} (T^c)_{i_2}^{\;\;\bar{i}_1} = (T^aT^b)_{i_2}^{\;\;\bar{i}_1} - (T^bT^a)_{i_2}^{\;\;\bar{i}_1}\,$.} 
    \label{fig:bbggHcolour}
\end{figure}

Just as before, we apply all the needed combinations of the $\bm{T}_i \cdot \bm{T}_j$ operators on the colour structures in $\bm{c}$ and extract the matrices $\mathcal{C}_{ij}$. We then know how to act with the pole operator $\bm{I}_{\bbggh}^{(1)}$ on the renormalised amplitude $A_R^{(L)}$ in this channel. Again, in the leading-colour approximation, the pole operator is diagonal, i.e. there is no mixing of different colour structures. However, contrary to $\bm{I}_{\bbqqh}^{(1)}$, it is not proportional to the identity matrix. We find:
\begin{equation*}
    \bm{I}_{\bbggh}^{(1)} = -N_c \frac{N(\eps)}{2}
    \begin{pmatrix}
        \mathrm{I}_1 & 0 & 0\\
        0 & \mathrm{I}_2 & 0\\
        0 & 0 & \mathrm{I}_3
    \end{pmatrix}\,,
\end{equation*}
where:
\begin{align}
    \mathrm{I}_1 = \mathrm{I}_2 &= \left(\frac{1}{\eps^2} + \frac{3}{4\eps} + \frac{\beta_0}{4 N_c \eps}\right) \left((-s_{23})^{-\eps} + (-s_{14})^{-\eps}\right) +\left(\frac{1}{\eps^2} + \frac{\beta_0}{2 N_c\eps} \right) (-s_{34})^{-\eps}\,, \nonumber \\
    \mathrm{I}_3 &= \left(\frac{1}{\eps^2} + \frac{3}{2\eps} \right) (-s_{12})^{-\eps} + \left(\frac{2}{\eps^2} + \frac{\beta_0}{2 N_c \eps} \right) (-s_{34})^{-\eps}\,.
\end{align}
As in the previous section, the last colour factor is always suppressed by $1/N_c$ with respect to the first two and we simply drop it. This completes the derivation of the $\bbggh$ leading-colour decomposition, Eq.~\ref{eq:colourdecomposition}, and its pole operators, Eq.~\ref{eq:I1bbggh}.

A careful reader might be alarmed by the presence of the $\beta_0/N_c$ term at leading colour. Indeed, since $\beta_0 = \frac{11}{3}C_A - \frac{4}{3} T_F n_f$ and $C_A = N_c$, we would expect only the $11/3$ contribution to survive. However, in most applications the number of light fermions circulating in closed loops is $n_f=4$ or $5$, thus $n_f/N_c \approx  \order{1}$. It is therefore reasonable to retain the $n_f$ term as well and the whole contribution is written in terms of the first $\beta$ function coefficient as $\beta_0/N_c$. This also provides the motivation for the decomposition in Eqs.~\ref{eq:NfDecomposition1L} and \ref{eq:NfDecomposition2L}.
\section{Pole structure of the QED process $0\to \ell \bar\ell \gamma \gamma^*$} \label{app:QEDpolestructure}
To derive the pole structure of the process $0\to \ell \bar\ell \gamma \gamma^*$ in Chapter~\ref{sec:QEDpaper}, we slightly depart from the procedure described above. In particular, in QED there is no colour structure, therefore applying the colour insertion operators would not make sense here. Instead, we follow the approach found in Refs.~\cite{Gardi:2009qi, Gardi:2009zv, Becher:2009cu, Becher:2009qa} and provide a brief outline below.

We renormalise the QED coupling constant by trading the bare coupling $\alpha_B$ for the renormalised one $\alpha_R$ through:
\begin{align}
    \label{eq:alpha-bare}
    \alpha_B = \alpha_R(\mu_R) \, Z_{\alpha}\bigl(\alpha_R(\mu_R) \bigr)  \, \mu_R^{2 \eps} \, S_{\eps} \,,
\end{align}
with $S_\eps= \mathrm{e}^{\eps\gamma_E} (4\pi)^{-\eps}$.
The renormalisation factor $Z_{\alpha}$ in the $\overline{\text{MS}}$ scheme is: \cite{Barnreuther:2013qvf,Bonciani:2021okt}
\begin{align}
    \label{eq:Za}
    Z_{\alpha}(\alpha) = 1 - \frac{\alpha}{4 \pi} \frac{\beta_0}{\eps} -
    \left(\frac{\alpha}{4 \pi}\right)^2 \left( -\frac{\beta_0^2}{\eps^2} + \frac{1}{2}\frac{\beta_1}{\eps} \right) + \mathcal{O}\bigl(\alpha^3\bigr) \,.
\end{align}
The QED $\beta$-function is defined from the renormalised coupling as:
\begin{align} \label{eq:beta_func_def}
\frac{\dd \alpha_{\rm R}(\mu_R)}{\dd \ln \mu_R} = \left[ -2 \, \eps + \beta\bigl(\alpha_{\rm R}(\mu_R)\bigr) \right]  \alpha_{\rm R}(\mu_R) \,,
\end{align}
and expanded as:
\begin{align} \label{eq:beta_func}
\beta( \alpha ) = -2 \, \frac{\alpha}{4 \pi}  \sum_{k\ge 0} \beta_k \left(\frac{\alpha}{4\pi} \right)^k \,,
\end{align}
with:
\begin{align} \label{eq:beta_coeffs}
\beta_0 = -\frac{4}{3} \nl \,, \qquad \qquad \beta_1 = - 4 \, \nl \,.
\end{align}
The photon wave function renormalisation factor is $Z_A=Z_\alpha$, which we include due to the external off-shell photon. The complete renormalisation procedure then is:
\begin{align}
    \mathcal{A}^\mu_R (\alpha_R) = Z_A^{\frac{1}{2}}(\alpha_R) \, \mathcal{A}^\mu_B (\alpha_B) \, ,
\end{align}
where $\alpha_B$ is expressed in terms of $\alpha_R$ through \cref{eq:alpha-bare}.

The IR poles of the renormalised amplitude factorise as~\cite{Catani:1998bh, Gardi:2009qi, Gardi:2009zv, Becher:2009cu, Becher:2009qa}:
\begin{align}
 \mathcal{A}^\mu_R (\alpha_R) = Z(\alpha_R) \,  \mathcal{F}^\mu(\alpha_R) \,,
\end{align}
so that $ Z(\alpha_R)$ captures all IR poles and $\mathcal{F}^\mu$ is a finite remainder.
We obtain the explicit two-loop expression of the IR factor $Z(\alpha_R)$ by
choosing QED parameters ($C_A=0$, $C_F=1$, and $T_F=1$) in the non-abelian gauge-theory expressions of \incite{Becher:2009qa}. We expand it as:
\begin{align}
    Z(\alpha) &= \sum_{k\ge0} Z^{(L)} \left(\frac{\alpha}{4\pi}\right)^L \,.
\end{align}
The coefficients $Z^{(L)}$ are expressed in terms of the anomalous dimension:
\begin{align}
    \Gamma &= \gamma^\text{cusp}\ln\left(\frac{-s_{12}}{\mu^2}\right)+2\gamma^l+\gamma^A \,,
\end{align}
and its derivative:
\begin{align}
    \Gamma^\prime &\coloneqq \frac{\partial\Gamma}{\partial\ln\mu} = -2\gamma^\text{cusp} \,.
\end{align}
Here, $\gamma^\text{cusp}$ is the cusp anomalous dimension, while $\gamma^l$ and $\gamma^A$ are the lepton's and the photon's collinear anomalous dimensions, respectively.
We expand all anomalous dimensions $y\in\{\Gamma,\gamma^i\}$ as:
\begin{align}
    y &= \frac{\alpha}{4\pi} \sum_{k\ge0} y_k \left(\frac{\alpha}{4\pi}\right)^k \,.
\end{align}
Their coefficients are listed in Appendix~\ref{app:renormconstants}. Finally, the coefficients of the IR factor $Z$ up to two loop are given by:
\begin{align}
    \label{eq:ir-pole-coeffs}
    Z^{(0)} &= 1 \,, &
    Z^{(1)} &= \frac{\Gamma_0^\prime}{4\eps^2}+\frac{\Gamma_0}{2\eps} \,, &
    Z^{(2)} &= \frac{{Z^{(1)}}^2}{2} -\frac{3\beta_0\Gamma_0^\prime}{16\eps^3}+\frac{\Gamma_1^\prime-4\beta_0\Gamma_0}{16\eps^2}+\frac{\Gamma_1}{4\eps} \,.
\end{align}
Putting together the subtraction of UV and IR poles, and expanding the resulting finite remainder $\mathcal{F}^{\mu}(\alpha_R)$ in $\alpha_R$ leads to the definitions in \cref{eqQED:finite-remainders}.

\renewcommand{\theequation}{D.\arabic{equation}}
\chapter{Renormalisation Constants} \label{app:renormconstants}
%\renewcommand{\theequation}{C.\arabic{equation}}
The bottom-quark Yukawa renormalisation constants are~\cite{Ahmed:2014pka,Mondini:2021nck}:
\begin{align}
r_1 & = -\frac{\beta_0}{2\eps}\,, \\
r_2 & = \frac{\beta_0^2}{4\eps^2} - \frac{\beta_1}{8\eps}\,, \\
s_1 & = -\frac{3 C_F}{2\eps} \,, \\
s_2 & = \frac{3}{8\eps^2}\big(3 C_F^2 + \beta_0 C_F \big) - \frac{1}{8\eps} \bigg( \frac{3 C_F^2}{2} + \frac{97}{6} C_F C_A -\frac{10}{3} C_F T_F n_f   \bigg) \,,
\end{align}
where the first two $\beta$ function coefficients are:
\begin{align}
    \beta_0 = & \;\frac{11}{3}C_A - \frac{4}{3} T_F n_f \,, \\
    \beta_1 = & \; \frac{34}{3} C_A^2 - \frac{20}{3} C_A T_F n_f - 4 C_F T_F n_f \,,
\end{align}
with $C_A = N_c$, $C_F = T_F(N_c^2-1)/N_c$.

The zeroth and first-order coefficients of the anomalous dimensions are given by~\cite{Becher:2009qa}: 
\begingroup
\allowdisplaybreaks
\begin{align}
\gamma_0^g = & \; -\frac{11}{3}C_A + \frac{4}{3} T_F n_f \,,   \\
\gamma_1^g = & \;  C_A^2 \left( -\frac{692}{27} + \frac{11\pi^2}{18} + 2 \zeta_3\right)
               + 4 C_F T_F n_f
               + C_A T_F n_f \left( \frac{256}{27} - \frac{2\pi^2}{9}\right) \,, \\
\gamma_0^q = & \; -3 C_F \,, \\
\gamma_1^q = & \; C_F^2 \left( -\frac{3}{2} + 2 \pi^2 - 24 \zeta_3 \right)
                  + C_F C_A \left( -\frac{961}{54} -\frac{11\pi^2}{6} + 26 \zeta_3 \right) \nn
             & \;  + C_F T_F n_f \left( \frac{130}{27} + \frac{2\pi^2}{3} \right) \,, \\
\gamma^l_0 = & -3 \,, \\
\gamma^l_1 = & -\frac{3}{2}+2\pi^2-24 \, \zeta_3+n_f\left(\frac{130}{27}+\frac{2}{3}\pi^2\right) \,, \\
\gamma^A_0 = & -\beta_0 \,, \\
\gamma^A_1 = & -\beta_1 \,, \\
\gamma_0^\cusp = & \; 4 \,, \\
\gamma_1^\cusp = & \; \left( \frac{268}{9} - \frac{4\pi^2}{3} \right) C_A -\frac{80}{9} T_F n_f \,.
\end{align}
\endgroup
We emphasise that while in QCD we have $N_c=3$ and $T_F = 1/2$, when working in QED one needs to set $C_A=0$, $C_F=1$ and $T_F=1$ in the expressions above.


\renewcommand{\theequation}{E.\arabic{equation}}
\chapter{One-Loop Results}
\label{app:oneloop}
In this Appendix, we collect the numerical results relevant to the amplitudes presented in Chapters~\ref{sec:Hbb} and \ref{sec:Wyj}. Tables~\ref{tab:benchmarkbare1L} and \ref{Wyjtab:benchmark1Lnf0bare} show the bare one-loop amplitudes (normalised by the tree-level amplitudes) for the two processes $\ppbbh$ and $\ppWgj$, respectively. Tables~\ref{tab:benchmarkfinremsq1L} and ~\ref{Wyjtab:benchmarkfinremsq1L} show the corresponding reduced squared tree-level amplitudes $\cH^{(0)}$ and reduced squared one-loop finite remainders (normalised by $\cH^{(0)}$).
\begin{table}[t!]
\centering
\begin{tabularx}{1.0\textwidth}{|C{0.7}|C{0.8}|C{0.5}|C{1.2}|C{1.2}|C{1.3}|C{1.3}|}
\hline
 $\bbggh$     & helicity & $\eps^{-2}$ & $\eps^{-1}$ & $\eps^{0}$ & $\eps^{1}$ & $\eps^{2}$ \\
\hline
$\hat A^{(1),1}$ & $++++$ & $ -3 $ & $ 3.07857 - 3.14159 i$ & $ 0.317351 + 8.42128 i$ & $ -1.25257 - 8.56907 i$ & $ 25.8294 - 4.35648 i $ \\
                 & $+++-$ & $ -3 $ & $ 3.07857 - 3.14159 i$ & $ -2.99786 - 1.02133 i$ & $ 2.86487 - 28.7164 i$ & $ 30.3093 - 26.3373 i $ \\
                 & $++-+$ & $ -3 $ & $ 3.07857 - 3.14159 i$ & $ -0.119814 + 8.67497 i$ & $ -1.43041 - 5.33656 i$ & $ 19.6373 - 0.110475 i $ \\
                 & $++--$ & $ -3 $ & $ 3.07857 - 3.14159 i$ & $ -6.51606 + 18.6156 i$ & $ -21.7849 + 24.0036 i$ & $ -24.6605 + 55.6878 i $ \\
\hline
$\hat A^{(1),n_f}$ & $++++$ & $ 0$ & $ 0$ & $ -0.005010 + 0.000779871 i$ & $ -0.00700827 - 0.0150298 i$ & $ 0.0109029 - 0.0163643 i $ \\
                   & $+++-$ & $ 0$ & $ 0$ & $ 0$ & $ 0$ & $ 0 $ \\
                   & $++-+$ & $ 0$ & $ 0$ & $ 0$ & $ 0$ & $ 0 $ \\
                   & $++--$ & $ 0$ & $ 0$ & $ -0.393552 + 0.138515 i$ & $ -0.793221 - 1.11035 i$ & $ 0.635641 - 1.48796 i $ \\
\hline
$\bbqqh$     & helicity & $\eps^{-2}$ & $\eps^{-1}$ & $\eps^{0}$ & $\eps^{1}$ & $\eps^{2}$ \\
\hline
$\hat A^{(1),1}$ & $+++-$ & $ -2 $ & $ 2.48840$ & $ -9.99430 - 8.95182 i$ & $ 2.20899 - 24.3401 i$ & $ 4.76962 - 27.6604 i $ \\
                 & $++-+$ & $ -2 $ & $ 2.48840$ & $ -8.43825 - 7.45006 i$ & $ 7.21741 - 24.6383 i$ & $ 13.6369 - 20.4876 i $ \\
\hline
$\hat A^{(1),n_f}$ & $+++-$ & $ 0$ & $ -0.666667$ & $ 0.726782 - 2.09440 i$ & $ 2.29387 + 2.28325 i$ & $ -2.54017 + 0.316127 i $ \\
                   & $++-+$ & $ 0$ & $ -0.666667$ & $ 0.726782 - 2.09440 i$ & $ 2.29387 + 2.28325 i$ & $ -2.54017 + 0.316127 i $ \\
\hline
\end{tabularx}
\caption{\label{tab:benchmarkbare1L} Numerical values of the bare $\bbggh$ and $\bbqqh$ partial amplitudes at one loop (normalised to the tree-level amplitude) at the kinematic point in 
Eq.~\eqref{eq:physicalpointHbbMomTwistor} for the four independent helicity configurations and the various closed fermion loops contributions. }
\end{table}

\begin{table}[t!]
\centering
\begin{tabularx}{0.85\textwidth}{|C{0.7}|C{1.1}|C{1.1}|C{1.1}|}
\hline
channel & $\mathcal{H}^{(0)}$ & $\mathrm{Re}\;\mathcal{H}^{(1),1}$ & $\mathrm{Re}\;\mathcal{H}^{(1),n_f}$  \\
\hline
$\mathbf{gg}$       & $ 1121.375369 $    & $ 4905.689964$ & $ 204.1069797 $ \\
$\mathbf{q\bar{q}}$ & $ 0.001095232986 $ & $ -0.008958148524$ & $ 0.0007959961305 $ \\
$\mathbf{\bar{q}q}$ & $ 0.001095232986 $ & $ 0.01182947634$ & $ 0.0007959961305 $ \\
$\mathbf{b\bar{b}}$ & $ 738.4111805 $ & $ 5948.275150$ & $ -2005.976183 $ \\
$\mathbf{\bar{b}b}$ & $ 774.9861507 $ & $ -8346.007933$ & $ -2253.325645 $ \\
$\mathbf{bb}/\mathbf{\bar{b}\bar{b}}$ & $ 71.81424881 $  & $ -678.1382010$ & $ -243.5040325 $ \\
\hline
\end{tabularx}
\caption{\label{tab:benchmarkfinremsq1L} Numerical values of the tree-level reduced squared amplitudes  $\mathcal{H}^{(0)}$ and 
one-loop reduced squared finite remainders $\mathcal{H}^{(1)}$ 
defined in Eqs.~\eqref{eq:channel_gg}-\eqref{eq:channel_BB} at the kinematic point in 
Eq.~\eqref{eq:physicalpointHbbMomTwistor} for  the closed fermion loops contributions and the scattering channels specified in Eq.~\eqref{eq:channel_definition}.}
\end{table}

\begin{table}[t!]
\centering
\begin{tabularx}{1.0\textwidth}{|C{0.7}|C{1.0}|C{0.6}|C{1.0}|C{1.2}|C{1.2}|C{1.3}|}
\hline
      & helicity & $\eps^{-2}$ & $\eps^{-1}$ & $\eps^{0}$ & $\eps^{1}$ & $\eps^{2}$ \\
\hline
$\hat A^{(1),1}_u$ & $\scriptstyle +++--+$ & -2 & 23.8477 & $-138.615 - 2.09370  i$ & $523.949 + 12.3666 i$ & $-1448.23 - 21.7701 i$ \\
                   & $\scriptstyle -++--+$ & -2 & 23.8477 & $-139.779 - 0.516164 i$ & $535.218 - 2.01397 i$ & $-1503.32 + 46.1044 i$ \\
\hline
$\hat A^{(1),1}_d$ & $\scriptstyle +++--+$ & -2 & 23.8477 & $-140.008 - 2.18806 i$  & $539.871 + 13.7461 i$ & $-1538.48 - 30.4669 i$ \\
                   & $\scriptstyle -++--+$ & -2 & 23.8477 & $-139.294 - 2.18046 i$  & $532.471 + 15.2170 i$ & $-1499.51 - 44.3866 i$ \\
\hline
$\hat A^{(1),1}_W$ & $\scriptstyle +++--+$ & -2 & 23.8477 & $-139.550 - 1.53563 i$  & $534.185 + 8.26368 i$ & $-1503.99 - 6.62167 i$ \\
                   & $\scriptstyle -++--+$ & -2 & 23.8477 & $-139.818 - 1.20381 i$  & $536.639 + 5.03856 i$ & $-1515.10 + 9.39205 i$ \\
\hline
$\hat A^{(1),1}_e$ & $\scriptstyle +++--+$ & -2 & 23.8477 & $-139.570 - 1.46851 i$  & $534.360 + 7.61926 i$ & $-1504.71 - 3.48177 i$ \\
                   & $\scriptstyle -++--+$ & -2 & 23.8477 & $-140.303 - 1.48855 i$  & $541.353 + 7.64165 i$ & $-1538.44 - 2.31498 i$ \\
\hline
\end{tabularx}
\caption{\label{Wyjtab:benchmark1Lnf0bare} 
Bare one-loop helicity sub-amplitudes (normalised to the tree-level amplitudes as in Eq.~\eqref{Wyjeq:treenorm}) without any closed fermion loop contribution  
for $\wpaj$ production in the $\mathbf{u\bar{d}}$ scattering channel 
evaluated at the kinematic point given in Eq.~\eqref{Wyjeq:PSpoint}. The results are shown for the two independent helicity configurations and obtained with $q_1 = p_3$ and $q_3 = p_1$ where $q_1$ ($q_3$) is the 
reference momentum for the photon (gluon) polarisation vector.
}
\end{table}

\begin{table}[t!]
\centering
\begin{tabularx}{1\textwidth}{|C{0.4}|C{1.2}|C{1.2}|C{1.2}|}
\hline
$W^+\gamma j$ & $\mathcal{H}^{(0)}  \; [\times 10^{-10}\,\mathrm{GeV}^{-4}] $ & $\mathrm{Re}\;\hat{\mathcal{H}}^{(1),1}$ & $\mathrm{Re}\;\hat{\mathcal{H}}^{(1),n_f}$  \\
\hline
$\mathbf{u\bar{d}}$ & 32.9224527109  & -20.4269208141 & 4.22462265354  \\
$\mathbf{\bar{d}u}$ & 35.8863373066  & -20.0350027848 & 4.22462265354  \\
$\mathbf{ug}      $ & 4.84655650134  & -26.9389515414 & 4.45445318051  \\
$\mathbf{gu}      $ & 15.2151742999  & -25.3235043118 & 4.37533965902  \\
$\mathbf{\bar{d}g}$ & 9.18270882925  & -28.3542876136 & 4.45445318051  \\
$\mathbf{g\bar{d}}$ & 26.4333120479  & -27.3120879601 & 4.37533965902  \\
\hline
\hline
$W^-\gamma j$ & $\mathcal{H}^{(0)}  \; [\times 10^{-10}\,\mathrm{GeV}^{-4}] $ & $\mathrm{Re}\;\hat{\mathcal{H}}^{(1),1}$ & $\mathrm{Re}\;\hat{\mathcal{H}}^{(1),n_f}$  \\
\hline
$\mathbf{d\bar{u}}$ & 48.5521763841  & -20.5759435967 & 4.22462265354  \\
$\mathbf{\bar{u}d}$ & 5.60724308955  & -25.0921274652 & 4.22462265354  \\
$\mathbf{dg}      $ & 0.161819754065 & -53.2745933316 & 4.45445318051  \\
$\mathbf{gd}      $ & 2.59919214772  & -35.7387232774 & 4.37533965902  \\
$\mathbf{\bar{u}g}$ & 0.471356750696 & -25.5067063821 & 4.45445318051  \\
$\mathbf{g\bar{u}}$ & 27.6357549618  & -32.8902240077 & 4.37533965902  \\
\hline
\end{tabularx}
\caption{\label{Wyjtab:benchmarkfinremsq1L} 
Reduced squared tree-level amplitude (absolute) and reduced squared one-loop finite remainders (normalised to the reduced squared tree amplitudes)
for the various closed fermion loop contributions and scattering channels of both $pp\to\wpaj$ and $pp\to\wmaj$ production,
evaluated at the kinematic point given in Eq.~\eqref{Wyjeq:PSpoint}.
}
\end{table}

\renewcommand{\theequation}{F.\arabic{equation}}
\chapter{Definition of the four-point integral families} \label{app:int_def}
For each two-loop integral family $T$ corresponding to one of the maximal topologies shown in \cref{fig:int-fams}, the Feynman integrals have the form:
\begin{equation}
	j^{T}(a_1, \ldots, a_9) = \mathrm{e}^{2 \eps \gamma_{E}} \int \frac{\mathrm{d}^{4-2\eps} k_1}{\mathrm{i} \pi^{2-\eps}} \frac{\mathrm{d}^{4-2\eps} k_2}{\mathrm{i} \pi^{2-\eps}} \frac{1}{D_{T,1}^{a_1} \ldots D_{T,9}^{a_9}} \,.
\end{equation}
The sets $\{D_{T,1}, \ldots, D_{T,9}\}$ contain seven (inverse) propagators and two ISPs ($a_8, a_9 \le 0$). 
For the maximal topologies under consideration, they are given by:\footnote{We use a naming convention analogous to that of \incite{Abreu:2020jxa}.}
\begin{itemize}
	\item penta-triangle, \textbf{mzz} configuration:
		\begin{align} \begin{aligned}
			\big\{k_1^2,(k_1+p_1+p_2+p_3)^2,(k_1+p_2+p_3)^2,(k_1+p_3)^2,k_2^2,(k_2-p_3)^2,\\(k_1+k_2)^2,(k_2-p_1-p_2-p_3)^2,(k_2-p_2-p_3)^2\big\} \,,
		\end{aligned} \end{align}
	\item penta-triangle, \textbf{zmz} configuration:
		\begin{align} \begin{aligned}
		\big\{k_1^2,(k_1-p_1)^2,(k_1+p_2+p_3)^2,(k_1+p_3)^2,k_2^2,(k_2-p_3)^2,(k_1+k_2)^2,\\(k_2+p_1)^2,(k_2-p_2-p_3)^2 \big\} \,,
		\end{aligned} \end{align}
	\item penta-triangle, \textbf{zzz} configuration:
		\begin{align} \begin{aligned}
			\big\{k_1^2,(k_1-p_1)^2,(k_1-p_1-p_2)^2,(k_1-p_1-p_2-p_3)^2,k_2^2,(k_2+p_1+p_2+p_3)^2, \\ (k_1+k_2)^2,(k_2+p_1)^2,(k_2+p_1+p_2)^2\big\} \,,
		\end{aligned} \end{align}
	\item planar double-box:
		\begin{align} \begin{aligned}
			\big\{k_1^2,(k_1-p_1)^2,(k_1-p_1-p_2)^2,k_2^2,(k_2+p_1+p_2+p_3)^2,(k_2+p_1+p_2)^2, \\ (k_1+k_2)^2,(k_1-p_1-p_2-p_3)^2,(k_2+p_1)^2\big\} \,,
		\end{aligned} \end{align}
	\item crossed double-box, \textbf{mz} configuration:
		\begin{align} \begin{aligned}
			\big\{k_1^2,(k_1+p_1+p_2+p_3)^2,(k_1+p_2+p_3)^2,k_2^2,(k_2-p_2)^2,(k_1+k_2)^2,\\ (k_1+k_2+p_3)^2,(k_1+p_3)^2,(k_2-p_1-p_2-p_3)^2\big\} \,,
		\end{aligned} \end{align}
	\item crossed double-box, \textbf{zz} configuration:
		\begin{align} \begin{aligned}
			\big\{k_1^2,(k_1-p_1)^2,(k_1-p_1-p_2)^2,k_2^2,(k_2-p_3)^2,(k_1+k_2)^2, \\ (k_1+k_2-p_1-p_2-p_3)^2,(k_1-p_1-p_2-p_3)^2,(k_2+p_1)^2\big\} \,.
		\end{aligned} \end{align}
\end{itemize}
%
We also use the one-loop (one-mass) box family, made of the following integrals:
\begin{equation}
	j^{\rm box}(a_1, a_2, a_3, a_4) = \mathrm{e}^{\eps \gamma_{E}} \int \frac{\mathrm{d}^{4-2\eps} k}{\mathrm{i} \pi^{2-\eps}} \frac{1}{D_{\mathrm{box}, 1}^{a_1} D_{\mathrm{box},2}^{a_2} D_{\mathrm{box},3}^{a_3} D_{\mathrm{box},4}^{a_4}} \,,
\end{equation}
with the four inverse propagators $D_{\mathrm{box},i}$:
	\begin{equation}
		\big\{k_1^2, (k_1-p_1)^2, (k_1-p_1-p_2)^2, (k_1-p_1-p_2-p_3)^2 \big\} \,.
	\end{equation}
Feynman's prescription for the imaginary parts of all propagators is implicit.

These family definitions (strictly with the ordering of inverse propagators and ISPs shown above) correspond to the integrals \texttt{j[family,$a_1,$\ldots]} that build the canonical MI bases provided in the \texttt{pure\_mi\_bases/} directory of our ancillary files~\cite{zenodo}. In this notation, each \texttt{j[...]} represents a Feynman integral within a given integral family, while the numbers $a_i$ refer to the powers of its propagators and ISPs.

\renewcommand{\theequation}{G.\arabic{equation}}
\chapter{Analytic continuation} \label{app:an_cont}
In Chapter~\ref{sec:QEDpaper}, we analytically continue the MPLs by adding a small positive (or negative) imaginary part to the MPL indices $l_i$ in \cref{eqQED:indices} whenever they fall between $0$ and $1$. The imaginary part of each index prescribes how to deform the integration contour around the pole associated with it. We do similarly for the logarithms in \cref{eqQED:logs}.
To this end, following \incite{Gehrmann:2002zr}, we change variables from $(s_{12},s_{23},s_4)$ to $(s_{12},s_{23},s_{13})$, with $s_4 = s_{12} + s_{23} + s_{13}$. We then add a small positive imaginary part to the latter variables, as
\begin{align} \label{eq:add_im}
s_{12} \longrightarrow s_{12} + \mathrm{i} \, c_{1} \, \delta \, , \qquad
s_{23} \longrightarrow s_{23} + \mathrm{i} \, c_{2} \, \delta  \, , \qquad
s_{13} \longrightarrow s_{13} + \mathrm{i} \, c_{3} \, \delta  \, , 
\end{align}
where $c_{1}$, $c_{2}$ and $c_{3}$ are arbitrary positive constants, and $\delta$ is a positive infinitesimal. 
Finally, we check whether this substitution gives a positive or negative imaginary part to each MPL index $l_i$.
This depends on the domain of the kinematic variables.
We focus on three kinematic regions which are of phenomenological interest. The analytic continuation for any other region may be obtained similarly.

\smallskip

\paragraph{Electron-line corrections to $e^- \mu^- \to e^- \mu^- \gamma$.}
To define the domain of the kinematic variables relevant for this application, 
we embed the four-particle off-shell process of \cref{eqQED:scatter} in the five-particle process $e^- \mu^- \to e^- \mu^- \gamma$. We then determine the kinematic constraints for the five-particle process (see e.g. Appendix~A of \incite{Chicherin:2021dyp}), and from them derive the constraints on the four-point off-shell kinematics. The result is
\begin{align}
\label{eq:region_emu-emugamma}
\mathcal{P}_{e\mu\to{e}\mu\gamma} \coloneqq \{\vec{s} \colon s_{12} < 0 \, \land \, s_{23} < 0 \, \land \, 0 < s_{13} < -s_{12} - s_{23} \} \,.
\end{align}
The MPL index $l_4 = - s_{12}/s_{23}$ is always negative in $\mathcal{P}_{{e}\mu\to{e}\mu\gamma}$, hence no analytic continuation is required. The other three indices may instead fall between $0$ and $1$. Let us study $l_1$. Changing variables from $s_4$ to $s_{13}$ and adding imaginary parts as in \cref{eq:add_im} gives
\begin{align}
l_1 = \frac{s_{12} + s_{13} + s_{23}}{s_{12}} +  \frac{\mathrm{i} \delta}{s_{12}^2} \left[ (c_2 + c_3) s_{12} - c_1 (s_{13} + s_{23}) \right] + \mathcal{O}\left(\delta^2\right) \,.
\end{align}
The imaginary part of $l_1$ may be either negative or positive in $\mathcal{P}_{{e}\mu\to{e}\mu\gamma} $. However, it is strictly negative in the subregion of $\mathcal{P}_{{e}\mu\to{e}\mu\gamma} $ where $0<l_1<1$. We therefore assign a negative imaginary part to $l_1$ whenever $0<l_1<1$ in $\mathcal{P}_{{e}\mu\to{e}\mu\gamma} $. The analysis of the other indices follows similarly, and is summarised in \cref{tab:an_cont}.
The arguments of the three logarithms in \cref{eqQED:logs} are positive in $\mathcal{P}_{e\mu\to{e}\mu\gamma}$.

\begin{table}
    \centering
    \begin{tabular}{cccc}
        \hline
        Index & $\mathcal{P}_{{e}\mu\to{e}\mu\gamma}$ & $\mathcal{P}_{{e}\bar{{e}}\to\gamma \gamma^*}$ & $\mathcal{P}_{\gamma^*\to e \bar{e} \gamma}$  \\
        \hline
        $l_1$  & $-$ & $+$ & $0$ \\
        $l_2$  & $-$ & $0$ & $0$ \\
        $l_3$  & $-$ & $0$ & $0$ \\
        $l_4$  & $0$ & $0$ & $0$ \\
        \hline
    \end{tabular}
    \caption{Imaginary parts of the MPL indices defined by \cref{eqQED:indices} in the two kinematic regions discussed in \cref{app:an_cont}. The symbol $+$ ($-$) denotes a positive (negative) imaginary part, while $0$ means no analytic continuation is needed.}
    \label{tab:an_cont}
\end{table}

\smallskip

\paragraph{Corrections to $e^- e^+ \to \gamma \gamma^*$.} The relevant domain of the kinematic variables in this case can be derived directly for the four-point kinematics, and is typically named the $s_{12}$ channel. It is given by 
\begin{align}
\label{eq:region_eebar}
\mathcal{P}_{e\bar{e}\to\gamma\gamma^*} \coloneqq \{\vec{s} \colon s_{23} < 0 \, \land \, s_{13} < 0 \, \land \, s_{12} > - s_{23} - s_{13} \} \,.
\end{align}
The MPL indices $l_2$, $l_3$ and $l_4$ can never fall between $0$ and $1$ in $\mathcal{P}_{e\bar{e}\to\gamma\gamma^*}$, and hence require no analytic continuation. We instead need to add a positive imaginary part to $l_1$. 
In this region also the logarithms in \cref{eqQED:logs} need to be analytically continued. The argument of $\log(s_{12}/s_4)$ is positive in $\mathcal{P}_{e\bar{e}\to\gamma\gamma^*}$. By adding imaginary parts to the arguments of the other logarithms and studying them where the arguments are negative in $\mathcal{P}_{e\bar{e}\to\gamma\gamma^*}$, we determine that the analytic continuation is achieved through the following replacements:
\begin{align}
\log(s_{23}/s_4) \longrightarrow \log(-s_{23}/s_{4})+ \mathrm{i} \pi \,, \qquad  \log(-s_4) \longrightarrow \log(s_4)- \mathrm{i} \pi \,.
\end{align}


\paragraph{Corrections to the decay $\gamma^* \to e^- e^+ \gamma$.} The relevant domain of the kinematic variables~is
\begin{align}
\label{eq:region_decay}
\mathcal{P}_{\gamma^*\to e \bar{e} \gamma} \coloneqq  \{ \vec{s} \colon s_{12} > 0 \, \land \, s_{23} > 0 \, \land \,  s_{13} > 0 \} \,.
\end{align}
All MPL indices $l_i$ in \cref{eqQED:indices} are either $l_i < 0$ or $l_i > 1$, hence no analytic continuation is required. The same holds for the first two logarithms in \cref{eqQED:logs}, whose arguments are positive. The only function which needs to be analytically continued is $\log(-s_4)$. We achieve this by replacing
\begin{align}
\log(-s_4) \longrightarrow \log(s_{4}) - \mathrm{i} \pi \,.
\end{align}

\smallskip

The information about the imaginary parts of the MPL indices can be fed into the publicly available libraries for evaluating these functions numerically, such as \texttt{FastGPL}~\cite{Wang:2021imw}, \texttt{GiNaC}~\cite{Bauer:2000cp, Vollinga:2004sn}, and \texttt{handyG}~\cite{Naterop:2019xaf}. This typically leads to longer evaluation times with respect to MPLs which do not need analytic continuation. We find that this is not an issue for the planned applications of our results (see \cref{secQED:performance}). Nonetheless, we note that a more performant evaluation may be achieved by tailoring the representation to the kinematic region of interest in such a way that no MPLs require analytic continuation. We refer the reader to Refs.~\cite{Gehrmann:2002zr, Gehrmann:2023etk} for a detailed discussion. 
\end{document}