\documentclass[main.tex]{subfiles}
\begin{document}
\chapter{Conclusions} \label{sec:conclusions}
In this thesis, we presented selected techniques needed for precision calculations of high-multiplicity loop scattering amplitudes. Such calculations constitute a crucial ingredient of the LHC precision programme, which aims to bring the theoretical uncertainties to the percent level and below. We started by discussing the general framework for computing predictions for physical observables using the machinery of QFT. Having established the key role of the scattering amplitude in this process, we described the challenges associated with their computation in practice. We dedicated Chapter~\ref{sec:tools} to a detailed discussion of a variety of tools employed to overcome these challenges. In particular, we showed how the use of finite fields helps us tackle the daunting algebraic complexity present in state-of-the-art calculations. We also noted the importance of the IBP reduction, which hugely reduces the number of integrals that need to be computed for the amplitude. This led us to the technique of differential equations, and in particular differential equations in the canonical form, which can be used to evaluate bases of pure master integrals with unexpected ease.

We applied the techniques presented in the first part of this thesis to three processes at the cutting edge of QCD and QED computations. First, we computed the two-loop helicity amplitudes for the production of the Higgs boson in association with a bottom-quark pair. This five-point process with a massive external leg is of great phenomenological interest, since an improved measurement of the bottom-quark Yukawa coupling could help constrain certain supersymmetric models which affect this coupling. In order to speed up the reconstruction of the analytic form of the rational coefficients from their numerical samples over finite fields, we implemented several optimisation tools which lower the complexity of this task. Moreover, exploiting the differential equation technique, we constructed a special function basis for the finite remainder of the amplitude which can be efficiently evaluated across the full phase space.

The second computation we tackled was the production of the $W$ boson in association with a photon and a jet. Here, the $W$ boson was assumed to further decay into a lepton pair, which allowed us to apply the familiar five-point kinematics with one off-shell leg to the scattering of six massless particles. Studying $W\gamma + n (\text{jet})$ production grants access to the $W W \gamma$ coupling, which can also be affected by new physics scenarios. In this work, we employed a new technique for simplifying the reconstructed functional coefficients based on a systematic search for the optimal rational parametrisation. In the future, this technique can be readily implemented also before reconstruction as an additional node of finite field operations, such that the search will not suffer from the algebraic complexity. Finally, in contrast to the previous set of amplitudes, we employed the tailored set of one-mass pentagon functions for the expansion of master integrals. These functions have the key advantage of being closed under the permutations of the massless momenta, which allows us to significantly reduce the number of kinematic points at which they have to be evaluated in order to serve a phenomenologically useful role.

Finally, we switched our focus to QED, computing the two-loop amplitudes for the scattering of a lepton pair with an off-shell and an on-shell photon. Our work completes the amplitude-level ingredients contributing to the N$^3$LO predictions of electron-muon scattering $e \mu \to e \mu$, which are required to meet the precision goal of the MUonE experiment. Here, the lower multiplicity meant that the reconstruction of analytic expressions from finite fields did not pose as serious a challenge as for the previous two processes. Instead, we focused on optimising the setup of the IBP reduction by exploiting numerical permutations of the IBP solutions obtained within a small set of families with specific orderings of external legs. This method allowed us to decrease the time and memory consumption of the IBP reduction stage, which becomes especially important in the case of processes with many integral families. Furthermore, we have constructed a basis of algebraically independent GPLs needed for the master integrals relevant to any scattering process of four massless particles with a single external off-shell leg up to two loops. This guarantees an efficient numerical evaluation and a compact analytic representation of the amplitudes.

Looking forward into the future, computations of amplitudes of higher multiplicity and loop order than the ones considered in this thesis are naturally going to present serious challenges. While we should be careful not to take the number of Feynman diagrams as a definitive measure of complexity, we can obtain its rough estimate by looking at how this number scales as we add more external legs to a given process. For example, adding an extra gluon to the $\bbqqh$ channel of $pp\to b\bar{b}H$ production in Chapter~\ref{sec:Hbb} increases the number of diagrams from 720 to 10142. Similarly, for the $\bbggh$ channel, the number grows from 3690 to 57478. Six-point kinematics with zero or one off-shell external legs means eight and nine Mandelstam invariants in the problem, respectively, which greatly increases the complexity even when using the finite field reconstruction technique. In terms of the IBP relations, while the three-loop, four-point kinematics with up to one off-shell leg has received significant attention already (see Ref.~\cite{Canko:2023yoe} and references therein), much less is known about the two-loop, six-point case even in a fully massless configuration~\cite{Henn:2022ydo, Henn:2021cyv}.

We would also like to point out the recent computation of the pure master integral bases for all two-loop integrals for five-particle kinematics with an off-shell leg~\cite{Abreu:2023rco}, which appeared in literature after the completion of the work presented in this thesis. The full set of pure bases for this kinematic configuration opens the door to a new range of computations, such as $pp \rightarrow H+2j$ and $pp \rightarrow W \gamma \gamma $ at NNLO, as well as the sub-leading colour corrections to the processes in Chapters~\ref{sec:Hbb} and~\ref{sec:Wyj}. As a preliminary estimate, we observe that the inclusion of the non-planar families increases the finite field reconstruction time by as much as an order of magnitude. We remark that this problem can be alleviated by using IBP relations simplified using syzygy relations~\cite{Gluza:2010ws, 10.1145/1993886.1993902, Schabinger:2011dz, Chen:2015lyz, Bohm:2017qme, Bosma:2018mtf, Boehm:2020zig}. We refer the reader to Ref.~\cite{Wu:2023upw} for details.

Overall, we believe that the work presented in this thesis represents a valuable contribution to the study of scattering amplitudes. We hope that the detailed introductory material serves as a useful reference for those new to the subject. With more and more data pouring in from the LHC and future colliders, it is clear that further breakthroughs in our computational techniques are needed to fully control the NNLO frontier and move towards the N$^3$LO one. The Les Houches wishlist~\cite{Huss:2022ful} continuously calls for new theoretical results, of which the scattering amplitudes are a key ingredient. Finally, we remark that, at some point in the future, obtaining analytic results for the amplitudes might become unfeasible and one should also consider pursuing a robust method for their numerical computation instead. Such numerical results can then be used further to produce predictions for the associated cross sections. From the perspective of phenomenology, this approach might become more efficient than first computing fully analytic amplitudes and subsequently evaluating them at chosen phase space points.
\end{document}