\documentclass[main.tex]{subfiles}

\begin{document}
\begin{enumerate}
    \item \textbf{Chapter 3 ($H\bar{b}b$). Put the computation in perspective from the experimental point of view} \\
%    \textcolor{gray}{2005.10277
%    \\
%    At the LHC, in the case of the bottom-quark Yukawa coupling ($y_b$), a direct sensitivity can
%be in principle achieved both via the $H \rightarrow \bar{b}b$ decay or via the associate production of a Higgs
%boson together with a $\bar{b}b$ pair. While the $H \rightarrow \bar{b}b$ decay has already been observed in conjunction
%with V H production [5, 6, 17–20], no dedicated SM analysis has ever been performed by the
%ATLAS and CMS collaboration in order to measure the $H\bar{b}b$ production process. Indeed, this
%process has an inclusive cross section that is comparable to the one of $H \bar{t}t$ production (e.g. ∼ 0.5
%pb at 13 TeV). However, at variance with $H \bar{t}t$ production, at least one b-jet has to be tagged
%in order to make it distinguishable from the inclusive Higgs-boson production process, whose
%production rate is ∼ 100 times larger than $H\bar{b}b$ production alone. The problem is that tagging
%a b-jet dramatically reduces the cross section, but as said this is an unavoidable procedure for
%obtaining a possible direct sensitivity on the bottom-quark Yukawa coupling. Without tagging
%any b-jet, even bottom-quark loops in ggF, which induce an indirect sensitivity on $y_b$, have a
%larger contribution: about $\approx6\%$ for the inclusive cross section and up to $\approx10\%$ for the Higgs
%boson at small transverse momentum [21–28].
%\\
%n our study, we demonstrate that the idea of directly extracting $y_b$ from the measurement of
%$H\bar{b}b$  at the LHC is substantially hopeless. The rates for this process are small and contaminated
%by terms that depend on $y_t$ and the $HZZ$ coupling. Reducing this contamination implies also
%a strong reduction of the cross section of the term depending only on $y_b$.}
%\\
%\textcolor{gray}{2011.13945
%\\
%Despite the large
%branching ratio of the Higgs decaying to the bottom pair, the $H\bar{b}b$ production eluded measurement
%until much later through the $V h, h \rightarrow \bar{b}b$ channel [6–8], bringing about sensitivity to the
%bottom-quark Yukawa, $y_b$, as well. The current sensitivity on $\kappa_b \propto y{b}/y_{SM}$
%b is of the order
%of $7\%$ and it is expected to improve to $2.2\%$ at HL-LHC [9]. Other direct probes to the
%Higgs couplings to the bottom quark can be envisaged through the measurements of the
%associated production of the Higgs with the bottom quark in the associated $bh$ or $\bar{b}bh$
%production channels.
%The $\bar{b}bh$ signal is sizeable at the LHC with a cross-section of about $0.5 pb$. Calculations of the $\bar{b}bh$ cross-section focusing on the contribution proportional to $y_b$ has been a
%developing effort, with improvements from including higher order contribution, matching
%and resumming bottom-mass effects, evaluation of four and five-flavour matching scheme
%and optimal scale choices for Monte Carlo implementation with parton showers [10–21].
%Despite the large inclusive rate, $\bar{b}bh$ production remains a challenging channel for experimental measurements. Given that the bulk of the signal contains only soft $p_T$ $b$-jets, which
%evade selection cuts, the signal drops by orders of magnitude after two, or even one, $b$-jets
%are explicitly tagged. It is even more challenging to achieve sensitivity on the $y_b$ coupling
%among all the amplitudes contributing to $\bar{b}bh$ production. Even with the large amount of
%luminosity that will be available at HL-LHC, the $y_b$ mediated diagrams contribute only a
%small fraction of the total cross section to the inclusive rate [20, 21].
%In this work we shall appeal to kinematic shapes, machine learning and game theory to
%glean information on $y_b$ from the associated production of the Higgs with a bottom-quark
%pair.}
%\\
%\textcolor{gray}{2101.10683
%\\
%Most importantly, its interaction strengths with relatively
%heavy fermions are not yet known precisely enough, in contrast to the interaction with gauge boson pairs, where the uncertainty is much lesser.} \\
%\hrule
From the perspective of phenomenology, $\ppbbh$ production at the LHC has been a subject of great interest due to its
potential in directly measuring the bottom-quark Yukawa coupling $y_b$.
In the SM, the coupling strengths of the Higgs boson to the fermions and vector bosons are proportional to their mass, causing the rate of the $b\bar{b}H$ production to be suppressed with respect to, for example,
Higgs production in gluon fusion ($gg\to H$) or vector boson fusion ($pp\to Hjj$), associated
production with a vector boson ($pp\to VH$), and associated production with a top-quark pair ($pp\to
t\bar{t}H$). 
\textcolor{red}{The inclusive $b \bar{b} H$ production cross section is approximately $0.5$ pb at $13$ TeV, however at least one $b$-jet needs to be tagged to distinguish this process from inclusive Higgs boson production, which lowers the detected rate by orders of magnitude~\cite{Pagani:2020rsg}. Recently, the possibility of isolating the relevant signal from the background using machine learning algorithms has been studied in literature~\cite{Grojean:2020ech, Konar:2021nkk}.}

In some scenarios, such as the Two Higgs Doublet Models (2HDM's) and the Minimal
Supersymmetric Standard Model (MSSM), the bottom-quark Yukawa coupling can be dramatically enhanced,
resulting in a considerable increase of the $b\bar{b}H$ production
rate~\cite{Balazs:1998nt,Dawson:2005vi}.  Thus, the study of the $b\bar{b}H$ production will allow
to constrain supersymmetric models and other extensions of the SM that modify the bottom-quark
Yukawa coupling. \textcolor{red}{The ratio of $y_b$ in a new physics scenario to $y_b$ in the SM, $\kappa_b = y_b / y_b^{\text{SM}}$, is currently known to 7\% and will be measured more precisely at high-luminosity LHC~\cite{Cepeda:2019klc}}. 
\item \textbf{Pg. 68 has the sentence `The presence of $b$-tagging further suppresses the bbH
production rate. Though the meaning can be reconstructed, the presence or not of
tagging does not change a rate, it changes detection} \\
See above - `suppresses the production rate' $\rightarrow$ `lowers the detected rate'.

\item \textbf{Summary of Chapter 3 ($H\bar{b}b$), sentence `To the best of our knowledge this is the first...'
can be broken down and clarified to further highlight the novelty of the result}
\\
In this chapter, we have presented an analytic form for the two-loop QCD amplitudes to the process
$pp\to b\bar{b}H$. \textcolor{red}{It is the first complete set of helicity
amplitudes provided for a $2\to 3$ scattering process with an off-shell leg. In contrast to the recent $pp\to Wb\bar{b}$ computation of Ref.~\cite{Badger:2021nhg}, which used the squared matrix element method (see Chapter~\ref{sec:Hbb}) and Mandelstam variables, we have constructed a rational parametrisation of the external kinematics in terms of momentum twistors. We have also improved on the function basis presented in Ref.~\cite{Badger:2021nhg} by identifying the missing relations among higher weight functions and products of lower weight ones. Moreover, we have used this basis to derive another one better suited to our finite remainders.} The remainders were then extracted from multiple evaluations over finite fields and IBP reduction, with a rational parametrisation of the external kinematics.

\item \textbf{Chapter 4 ($W^\pm \gamma j$), again put in context, e.g. there seems to be one loop EW corrections
that might be more relevant than those computed, are these known?}
\\
\textcolor{red}{Our work opens the path for precision predictions for $pp \rightarrow W^\pm \gamma j$ production at NNLO accuracy in the strong coupling. Naturally, a detailed phenomenological study would also include EW corrections, which can dominate the QCD ones in certain phase space regions of single or double vector boson production. For example, for the process $pp \rightarrow W^\pm j$, the NLO EW corrections can reach up to 50\% of the LO, as compared to 10\% for the NNLO QCD ones~\cite{Tricoli:2020uxr, Gehrmann-DeRidder:2017mvr, Boughezal:2015dva, Boughezal:2016dtm, Lindert:2017olm}. Although less pronounced, NLO EW effects are also significant for $pp \rightarrow W^\pm \gamma$ production~\cite{Cridge:2021hfr, Denner:2014bna, Accomando:2005ra, Grazzini:2015nwa, Campbell:2021mlr}. Therefore, it will be of great importance to study such corrections to the $pp \rightarrow W^\pm \gamma j$ process as well in order to achieve more reliable predictions across the full phase space.}

\item \textbf{Given the title contains “high multiplicity”, maybe comment on the Summary what
would take to tackle higher-legs amplitude and how the “amount of work” would
scale}

\textcolor{red}{Looking forward into the future, computations of amplitudes of higher multiplicity and loop order than the ones considered in this thesis are naturally going to present serious challenges. While we should be careful not to take the number of Feynman diagrams as a definitive measure of complexity, we can obtain its rough estimate by looking at how this number scales as we add more external legs to a given process. For example, adding an extra gluon to the $\bbqqh$ channel of $pp\to b\bar{b}H$ production in Chapter~\ref{sec:Hbb} increases the number of diagrams from 720 to 10142. Similarly, for the $\bbggh$ channel, the number grows from 3690 to 57478. Six-point kinematics with zero or one off-shell external legs means eight and nine Mandelstam invariants in the problem, respectively, which greatly increases the complexity even when using the finite field reconstruction technique. In terms of the IBP relations, while the three-loop, four-point kinematics with up to one off-shell leg has received significant attention already (see~\cite{Canko:2023yoe} and references therein), the IBP relations for the two-loop, six-point case remain unknown even in a fully massless configuration.}

We would also like to point out the recent computation of the pure master integral bases for all two-loop integrals for five-particle kinematics with an off-shell leg~\cite{Abreu:2023rco}, which appeared in literature after the completion of the work presented in this thesis. The full set of pure bases for this kinematic configuration opens the door to a new range of computations, such as $pp \rightarrow H+2j$ and $pp \rightarrow W \gamma \gamma $ at NNLO, as well as the sub-leading colour corrections to the processes in Chapters~\ref{sec:Hbb} and~\ref{sec:Wyj}. \textcolor{red}{As a preliminary estimate, we observe that the inclusion of non-planar families increases the number of integrals in the Laporta IBP system roughly by an order of magnitude. The finite field reconstruction time increases accordingly. We remark that this problem can be mitigated by using IBP relations simplified using so-called syzygy relations~\cite{Gluza:2010ws, 10.1145/1993886.1993902, Schabinger:2011dz, Chen:2015lyz, Bohm:2017qme, Bosma:2018mtf, Boehm:2020zig}. We refer the reader to Ref.~\cite{Wu:2023upw} for details.}

Overall, we believe that the work presented in this thesis represents a valuable contribution to the study of scattering amplitudes. We hope that the detailed introductory material serves as a useful reference for those new to the subject. With more and more data pouring in from the LHC and future colliders, it is clear that further breakthroughs in our computational techniques are needed to fully control the NNLO frontier and move towards the N$^3$LO one. The Les Houches wishlist~\cite{Huss:2022ful} continuously calls for new theoretical results, of which the scattering amplitudes are a key ingredient. \textcolor{red}{Finally, we remark that at some point obtaining analytic results for the amplitudes might become unfeasible and one should also consider pursuing a robust method for their numerical evaluation instead. Such numerical results can then be used further to produce predictions for the associated cross sections. From the perspective of phenomenology, this approach might become more efficient than computing fully analytic amplitudes and subsequently evaluating them at chosen phase-space points.}

\bibliographystyle{JHEP}
\bibliography{bibliography_total}

\end{enumerate}
\end{document}