\documentclass[twoside,frontopenright,halfspacing, openany]{ip3thesis}
\input{preamble}
\input{ExtraDefinitions}
\newcolumntype{C}[1]{>{\hsize=#1\hsize\centering\arraybackslash}X}%
\usepackage{subfiles}


\begin{document}
\title{Techniques for high-multiplicity scattering amplitudes with an off-shell leg.}
\author{Jakub Kry\'s}
\researchgroup{Institute for Particle Physics Phenomenology}
\maketitlepage*

\begin{abstract}
%
	In this thesis, we present state-of-the-art techniques for the computation of scattering amplitudes in Quantum Field Theories. Following an introduction to the topic, we present a robust framework that enables the computation of cutting-edge amplitudes directly relevant to modern particle physics phenomenology at the Large Hadron Collider and beyond. We describe in detail the use of finite fields to bypass the algebraic complexity of such computations, as well as the method of differential equations to evaluate Feynman integrals. We apply our framework to calculate the two-loop amplitudes contributing to three process: Higgs boson production in association with a bottom-quark pair, $W^\pm$ boson production with a photon and a jet, as well as lepton-pair scattering with an off-shell and an on-shell photon in massless QED. Finally, we draw our conclusions and discuss directions for future progress of amplitude computations.
%
\end{abstract}

\disableprotrusion
\tableofcontents*
%\listoffigures
%\listoftables
\enableprotrusion

\begin{declaration*}
%
	The work in this thesis is based on joint research carried out in the Department of
	Physics at Durham University (UK), as well as in the Department of Physics at the University of Turin (Italy). Chapter~\ref{sec:Hbb} is based on Ref.~\cite{Badger:2021ega}, Chapter~\ref{sec:Wyj} on Ref.~\cite{Badger:2022ncb} and Chapter~\ref{sec:QEDpaper} on Ref.~\cite{Badger:2023xtl}. No part of this thesis has been submitted elsewhere for any degree or qualification.  
%
\end{declaration*}

\begin{acknowledgements*}
%
	Most of all, I would like to thank my supervisor, Simon Badger, for his continuous guidance over the last couple of years, stretching back to our time in Durham. Without his keen help, the course of my PhD would have been much rougher.
 
    I am indebted to my collaborators: Simone Zoia, Bayu Hartanto, Ryan Moodie and Francesco Sarandrea, for patiently answering my endless and extremely specific questions, as well as for providing occasional IT support.
    
    Finally, I thank my fellow PhD students in Torino for making my time there enjoyable and for tirelessly explaining convoluted concepts of Italian grammar.
    
    I wish all a fruitful and happy future (and no sign mistakes when permuting $\tr_5$).
%
\end{acknowledgements*}

\begin{epigraph*}
%
%Each of us\\
%A cell of awareness\\
%Imperfect and incomplete\\
%Genetic blends\\
%With uncertain ends\\
%On a fortune hunt that's far too fleet
%	\source{Freewill}{Rush}
%
\end{epigraph*}

%\dedicationtext{This thesis is dedicated to}
%\begin{dedication*}
%%
%	Someone special
%	\also[and]{that other guy}
%%
%\end{dedication*}

%\cleardoublepage

\subfile{Intro}
\subfile{Tools}
\subfile{Hbb}
\subfile{Wgammaj}
\subfile{QEDpaper}
%\subfile{Selfdual}
\subfile{Conclusions}

\appendix
\subfile{AppendixTotal}
%\subfile{Hbbappendix}
%\subfile{Wyjappendix}
%\subfile{PolesAppendix}

\Urlmuskip=0mu plus 5mu\relax
%\raggedright
\bibliographystyle{JHEP}
\bibliography{bibliography_total}

\end{document}
